### 2016-03-30 3dv-2015authorkit/latex/egpaper_final.tex
initial commit

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{3dv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\threedvfinalcopy % *** Uncomment this line for the final submission

\def\threedvPaperID{****} % *** Enter the 3DV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifthreedvfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for 3DV Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous 3DV  abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Please follow the steps outlined below when submitting your manuscript to
the IEEE Computer Society Press.  This style guide now has several
important modifications (for example, you are no longer warned against the
use of sticky tape to attach your artwork to the paper), so all authors
should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

By submitting a manuscript to 3DV, the authors assert that it has not been
previously published in substantially similar form. Furthermore, no paper
which contains significant overlap with the contributions of this paper
either has been or will be submitted during the 3DV 2015 review period to
{\bf either a journal} or any conference or any
workshop.
 {\bf Papers violating this condition will be rejected.}

If there are papers that may appear to the reviewers
to violate this condition, then it is your responsibility to: (1)~cite
these papers (preserving anonymity as described in Section 1.6 below),
(2)~argue in the body of your paper why your 3DV paper is non-trivially
different from these concurrent submissions, and (3)~include anonymized
versions of those papers in the supplemental material.

\subsection{Paper length}
3DV papers should be no longer than 8 pages, excluding references, and no longer than 
9 pages in total length. Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\threedvfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $097.15$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics.%: \url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith, it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors12} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2012 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a techreport for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors12b}''.  Then submit the techreport as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the 3DV70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.

FAQ: Are acknowledgments OK?  No.  Leave them for the final copy.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

%For this citation style, keep multiple citations in numerical (not
%chronological) order, so prefer \cite{Alpher03,Alpher02,Authors12} to
%\cite{Alpher02,Alpher03,Authors12}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.  Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this find the line (around
line 23)  
\begin{verbatim}
%\ifthreedvfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 47
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors12}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Color is valuable, and will be visible to readers of the electronic copy.
However ensure that, when printed on a monochrome printer, no important
information is lost by the conversion to grayscale.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2016-03-30 paper.tex
initial commit

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{3dv-2015authorkit/latex/3dv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%\threedvfinalcopy % *** Uncomment this line for the final submission

\def\threedvPaperID{****} % *** Enter the 3DV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifthreedvfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{A Large-Scale 3D Object Recognition dataset}

\author{Thomas S{\o}lund\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Anders Glent Buch, Norbert Kr\"u{}ger\\
M\ae{}rsk Mc-Kinney M\o{}ller Institute,\\
University of Southern Denmark,\\
DK-5230 Odense, Denmark \\
{\tt\small anbu,norbert@mmmi.sdu.dk}
\and
Knut Conradsen, Henrik Aanæs\\
Department of Applied Mathematics\\ and Computer Science,\\ 
Technical University of Denmark\\
DK-2800 Kgs. Lyngby, Denmark\\
{\tt\small knco,aanes@dtu.dk}
}

\maketitle
% \thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous 3DV abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

%-------------------------------------------------------------------------
\section{Related work}
The UWA dataset by Mian et.al. \cite{Mian2006}, \cite{Mian2010} is one of the best known datasets for 3D pose estimation algorithm evaluation. The dataset is composed of four full object models and 50 real scenes captures with a laser scanner which containing incomplete instances of the objects. Each scene contains three or four object models which results in much clutter and occlusion. The amount of occlusion and clutter in each scene is not provided. The four object models are generated with a multi-view registration algorithm. Each object model contain more than 100000 mesh vertices and posses good and distinctive shape features with non-uniform surfaces and ambiguities. The object models and scenes has pre-estimated normals and no color/texture. The dataset contains full 6D ground truth poses for each object as the only evaluation data type.

The Queens Lidar dataset \cite{Taati2011}, \cite{Taati2007} is constructed like the UWA dataset with a laser scanner and consists of five object models and 80 real scenes take from one viewpoint. Like the UWA dataset, the Queens Lidar dataset contains no color information but the scenes has larger variation compared to the UWA dataset with one to five object models present in the scenes. The five object models has pre-estimated normals but is only provided as a point representation. The dataset contains full 6D ground truth poses for each object as the only evaluation data.

The Queens Stereo dataset \cite{Taati2011}, \cite{Taati2007} contains five full object models and 100 real scenes created with a stereo camera and standard stereo reconstruction. The dataset is taken from one viewpoint. Each scene contains three object models with no color, normal, occlusion or clutter information available. Like the Queens Lidar dataset the object models is represented with points and no vertices. The dataset contains full 6D ground truth poses for each object as the only evaluation data.

The Bologna 1 \& 2 dataset \cite{Salti2014}, \cite{Tombari2010} contains six full object models and 45 synthetic scenes. All scenes is construct a synthetic scenes with models from the Stanford 3D Scanning Repository. Each 45 scenes are created by applying a random transformation to a random subset of object model and store the scene. The difference between the Bologna 1 and Bologna 2 dataset are that Bologna 2 is re-sampled 1/8 of the original point density. The fact that it is a synthetic dataset results in 100 percent accurate 6D ground truth data.

The Bologna 3 dataset \cite{Salti2014}, \cite{Tombari2010} contains eight models and 15 scenes. Each scenes are acquired with spacetime stereo technique and contains both color and surface normal information. Each scene contains two object models and additional objects to create clutter and occlusion. The eight models are single view object templates with color and estimated normals in mesh representation. The dataset contains full 6D pose estimates as ground truth. Their exist no data on occlusion and clutter estimates.

The Bologna 4 dataset \cite{Salti2014}, \cite{Tombari2010} contains eight models and 16 scenes. As Bologna 3, this dataset is acquired with spacetime stereo techniques and containing color and normal data for both the object models and the scenes. The dataset includes object models with highly similar shapes but different textures. Each scene contains two object models and additional objects to create clutter and occlusion. The eight models are single view object templates with color and estimated normals in mesh representation. The dataset contains full 6D pose estimates as ground truth. Their exist no data on occlusion and clutter estimates.

The Bologna 5 dataset \cite{Salti2014}, \cite{Tombari2010} contains six object models and 16 scenes. The dataset is acquired with a Microsoft Kinect sensor and includes color and normal information for both the object models and scenes. The provided object models is a set of object templates taken from different views. With a proper mesh registration algorithm a full object model can be created. The dataset contains full 6D pose estimates as ground truth. Their exist no data on occlusion and clutter estimates.

The Vienna Kinect dataset \cite{Aldoma2012} contains 35 full object models and 50 scenes. Each scene is acquired with a Microsoft Kinect sensor and includes color information but no pre-estimated normals. All scenes is table top scenes with limited occlusion and clutter. The object models in each scene is distThe 35 object models are full represented mesh models without color but includes pre-estimated normals. 
The dataset contains full 6D pose estimates as ground truth. Their exist no data on occlusion and clutter estimates.

TUM dataset \cite{Rodola2013}\\

RGB-D Dataset V1 \cite{Lai2011}, \cite{Lai2012}\\

RGB-D Dataset V2 \cite{Lai2014}\\ 
%------------------------------------------------------------------------
\section{Experimental design}

%-------------------------------------------------------------------------
\section{Benchmark}

%-------------------------------------------------------------------------
\section{Evaluation}

%-------------------------------------------------------------------------
\section{Discussion}

%-------------------------------------------------------------------------
\section{Conclusion}

%-------------------------------------------------------------------------

{\small
\bibliographystyle{3dv-2015authorkit/latex/ieee}
\bibliography{bib}
}

\end{document}

### 2016-04-10 paper.tex
intro

@@
 
-\author{Thomas S{\o}lund\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
+%\author{Thomas S{\o}lund\\
+%Institution1\\
+%Institution1 address\\
+%{\tt\small thso@dti.dk}
 % For a paper whose authors are all at the same institution,
@@
 % To save space, use either the email address or home page, not both
-\and
-Anders Glent Buch, Norbert Kr\"u{}ger\\
-M\ae{}rsk Mc-Kinney M\o{}ller Institute,\\
-University of Southern Denmark,\\
-DK-5230 Odense, Denmark \\
-{\tt\small anbu,norbert@mmmi.sdu.dk}
-\and
-Knut Conradsen, Henrik Aanæs\\
-Department of Applied Mathematics\\ and Computer Science,\\ 
-Technical University of Denmark\\
-DK-2800 Kgs. Lyngby, Denmark\\
-{\tt\small knco,aanes@dtu.dk}
-}
+%\and
+%Anders Glent Buch, Norbert Kr\"u{}ger\\
+%M\ae{}rsk Mc-Kinney M\o{}ller Institute,\\
+%University of Southern Denmark,\\
+%DK-5230 Odense, Denmark \\
+%{\tt\small anbu,norbert@mmmi.sdu.dk}
+%\and
+%Knut Conradsen, Henrik Aanæs\\
+%Department of Applied Mathematics\\ and Computer Science,\\ 
+%Technical University of Denmark\\
+%DK-2800 Kgs. Lyngby, Denmark\\
+%{\tt\small knco,aanes@dtu.dk}
+%}
 
 \maketitle
-% \thispagestyle{empty}
+%\thispagestyle{empty}
 
@@
 \begin{abstract}
-   The ABSTRACT is to be in fully-justified italicized text, at the top
-   of the left-hand column, below the author and affiliation
-   information. Use the word ``Abstract'' as the title, in 12-point
-   Times, boldface type, centered relative to the column, initially
-   capitalized. The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous 3DV abstracts to get a feel for style and length.
+ To be written...........
 \end{abstract}
@@
 \section{Introduction}
+The ability to recognise objects in range images is a fundamental research area in computer vision with many different application areas.
+With continually introduction of new affordable 3D sensors for different applications, the ability to localize and recognize rigid and no rigid objects are a attractive and unavoidable technology in the future.
+Applications areas such as robotic assembly, bin-picking, mobile manipulation, biometric analysis, tracking and intelligent surveillance all benefits from 3D data for recognizing and localizing objects.
+Mainly, because the third dimension are explicit given and not inferred as known from 2D object recognition and pose estimation.
+In the last decades a huge effort in 2D object recognition and classification has been going on, where methods have been evaluated on large-scale dataset like the PASCAL Visual Object Challenge (VOC) \cite{Everingham2014}, ImageNet \cite{Imagenet2009}.
+The ability to evaluate on a large-scale dataset has proven valuable in the future algorithm development after the release of the PASCAL VOC and ImageNet datasets \cite{Everingham2014}.
+In 3D object recognition and pose estimation there still lacks a large-scale dataset in order to evaluate algorithms.
+Until today 3D object recognition and pose estimations has been evaluated at a couple of smaller datasets namely the UWA \cite{Mian2006}, Queens \cite{Taati2007}, Bologna \cite{Salti2014},\cite{Tombari2010}, Vienna Kinect\cite{Aldoma2012}, TUM \cite{Rodola2013}, TUM-LineMod\cite{Hinterstoisser2012}, BigBird\cite{BigBIRD} and RGB-D dataset version 1 \& 2\cite{Lai2011}, \cite{Lai2014}.
+In this work we present a evaluation of local shape features and present a new large-scale dataset consisting of 50 objects and 300 scenes.
+The new dataset is recorded systematically using a setup with a industrial robot, a structured light sensor and a Kinect V2 sensor, which records data from 11 different view points.
+Each scene consists of 10 objects  automatic take with two different sensors, which results in a dataset with around 66000 unique object poses.
 
-%-------------------------------------------------------------------------
-\section{Related work}
-The UWA dataset by Mian et.al.
+%and pose estimation \cite{Viksten09}, \cite{Hinterstoisser2012}, this kind of scientific validations of results still lacks in 3D object recognition. 
+%2D object recognition is well studied lacking with 3D. Keypoint comparison Aan{\ae}s et.al. \cite{Aanaes2011}
+
+%We study the performance of the top six local shape features and one global descriptor 
+%Limitations in current dataset and algorithms. Feature rich objects not flat or cylindrical objects
+
+%The UWA dataset by Mian et.al.
 \cite{Mian2006}, \cite{Mian2010} is one of the best known datasets for 3D pose estimation algorithm evaluation.
@@
 
-The Queens Lidar dataset \cite{Taati2011}, \cite{Taati2007} is constructed like the UWA dataset with a laser scanner and consists of five object models and 80 real scenes take from one viewpoint.
+%The Queens Lidar dataset \cite{Taati2011}, \cite{Taati2007} is constructed like the UWA dataset with a laser scanner and consists of five object models and 80 real scenes take from one viewpoint.
 Like the UWA dataset, the Queens Lidar dataset contains no color information but the scenes has larger variation compared to the UWA dataset with one to five object models present in the scenes.
@@
 
-The Queens Stereo dataset \cite{Taati2011}, \cite{Taati2007} contains five full object models and 100 real scenes created with a stereo camera and standard stereo reconstruction.
+%The Queens Stereo dataset \cite{Taati2011}, \cite{Taati2007} contains five full object models and 100 real scenes created with a stereo camera and standard stereo reconstruction.
 The dataset is taken from one viewpoint.
@@
 
-The Bologna 1 \& 2 dataset \cite{Salti2014}, \cite{Tombari2010} contains six full object models and 45 synthetic scenes.
+%The Bologna 1 \& 2 dataset \cite{Salti2014}, \cite{Tombari2010} contains six full object models and 45 synthetic scenes.
 All scenes is construct a synthetic scenes with models from the Stanford 3D Scanning Repository.
@@
 The fact that it is a synthetic dataset results in 100 percent accurate 6D ground truth data.
-
-The Bologna 3 dataset \cite{Salti2014}, \cite{Tombari2010} contains eight models and 15 scenes.
+%The Bologna 3 dataset \cite{Salti2014}, \cite{Tombari2010} contains eight models and 15 scenes.
 Each scenes are acquired with spacetime stereo technique and contains both color and surface normal information.
@@
 Their exist no data on occlusion and clutter estimates.
-
-The Bologna 4 dataset \cite{Salti2014}, \cite{Tombari2010} contains eight models and 16 scenes.
+%The Bologna 4 dataset \cite{Salti2014}, \cite{Tombari2010} contains eight models and 16 scenes.
 As Bologna 3, this dataset is acquired with spacetime stereo techniques and containing color and normal data for both the object models and the scenes.
@@
 Their exist no data on occlusion and clutter estimates.
-
-The Bologna 5 dataset \cite{Salti2014}, \cite{Tombari2010} contains six object models and 16 scenes.
+%The Bologna 5 dataset \cite{Salti2014}, \cite{Tombari2010} contains six object models and 16 scenes.
 The dataset is acquired with a Microsoft Kinect sensor and includes color and normal information for both the object models and scenes.
@@
 Their exist no data on occlusion and clutter estimates.
-
-The Vienna Kinect dataset \cite{Aldoma2012} contains 35 full object models and 50 scenes.
+%The Vienna Kinect dataset \cite{Aldoma2012} contains 35 full object models and 50 scenes.
 Each scene is acquired with a Microsoft Kinect sensor and includes color information but no pre-estimated normals.
@@
 The object models in each scene is distThe 35 object models are full represented mesh models without color but includes pre-estimated normals.
-The dataset contains full 6D pose estimates as ground truth. Their exist no data on occlusion and clutter estimates.
-
-TUM dataset \cite{Rodola2013}\\
-
-RGB-D Dataset V1 \cite{Lai2011}, \cite{Lai2012}\\
-
-RGB-D Dataset V2 \cite{Lai2014}\\ 
-%------------------------------------------------------------------------
-\section{Experimental design}
+%The dataset contains full 6D pose estimates as ground truth. Their exist no data on occlusion and clutter estimates.
+%TUM dataset \cite{Rodola2013}\\
+%RGB-D Dataset V1 \cite{Lai2011}, \cite{Lai2012}\\ 
+%RGB-D Dataset V2 \cite{Lai2014}\\
 
 %-------------------------------------------------------------------------
-\section{Benchmark}
+\section{Related work}
+%We are not considering learning approaches
+\textbf{Local Shape features:}\\
+
+Spin Images \cite{Johnson1999}\\
+Froome \etal \cite{Frome2004} presented a local descriptor 3D shape context.
+USC \cite{usc2010}\\
+
+FPFH \cite{Fpfh2009}\\
+ESAC \cite{Ecsad2015}\\
+ROPS \cite{Guo2013}\\
+SHOT \cite{Salti2014}\\
+NDHIST\\
+PPF \cite{Drost2010}\\
+SHOT \cite{Tombari2010}\\
+
+Feature Fusion \cite{Buch2016}\\
+Feature comparision Yulan et.al. \cite{Guo2015}
+
+%------------------------------------------------------------------------
+%\section{Experimental design}
 
 %-------------------------------------------------------------------------
-\section{Evaluation}
+%\section{Benchmark}
 
 %-------------------------------------------------------------------------
-\section{Discussion}
+%\section{Evaluation}
 
 %-------------------------------------------------------------------------
-\section{Conclusion}
+%\section{Discussion}
+
+%-------------------------------------------------------------------------
+%\section{Conclusion}
 
@@
 }
-
 \end{document}

### 2016-06-21 3dv2016authorkit/latex/egpaper_final.tex
added 3dv 2016 template

--- 2016-03-30 3dv-2015authorkit/latex/egpaper_final.tex
@@
 which contains significant overlap with the contributions of this paper
-either has been or will be submitted during the 3DV 2015 review period to
+either has been or will be submitted during the 3DV 2016 review period to
 {\bf either a journal} or any conference or any
@@
 \subsection{Paper length}
-3DV papers should be no longer than 8 pages, excluding references, and no longer than 
-9 pages in total length. Overlength papers will simply not be reviewed.  This includes papers
-where the margins and formatting are deemed to have been significantly
-altered from those laid down by this style guide.  Note that this
-\LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for
-supervised revisions of manuscripts.  The reviewing process cannot determine
-the suitability of the paper for presentation in eight pages if it is
-reviewed in eleven.
+3DV papers should be no longer than 8 pages, excluding references.
+The references section will not be included in the page count, and
+there is no limit on the length of the references section. Overlength
+papers will simply not be reviewed.  This includes papers where the
+margins and formatting are deemed to have been significantly altered
+from those laid down by this style guide.  Note that this \LaTeX\ 
+guide already sets figure captions and references in a smaller font.
+The reason such papers will not be reviewed is that there is no
+provision for supervised revisions of manuscripts.  The reviewing
+process cannot determine the suitability of the paper for presentation
+in eight pages if it is reviewed in eleven.
 

### 2016-06-21 3dv2016authorkit/latex/egpaper_for_review.tex
added 3dv 2016 template

--- 2016-06-21 3dv2016authorkit/latex/egpaper_final.tex
@@
 % run, let it finish, and you should be clear).
-%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
 
-\threedvfinalcopy % *** Uncomment this line for the final submission
+%\threedvfinalcopy % *** Uncomment this line for the final submission
 
@@
 \ifthreedvfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
 \begin{document}
@@
 \maketitle
-%\thispagestyle{empty}
+% \thispagestyle{empty}
 
@@
 {\bf either a journal} or any conference or any
-workshop.
- {\bf Papers violating this condition will be rejected.}
+workshop.  {\bf Papers violating this condition will be rejected}.
 
@@
 an alternative to equation numbers).  All authors will benefit from reading
-Mermin's description of how to write mathematics.%: \url{http://www.pamitc.org/documents/mermin.pdf}.
+Mermin's description of how to write mathematics:
+\url{http://www.pamitc.org/documents/mermin.pdf}.
 
@@
 
-FAQ: Are acknowledgments OK?  No.  Leave them for the final copy.
+FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.
 
@@
 
-All printed material, including text, illustrations, and charts, must be kept
-within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
-high.  Page numbers should be in footer with page numbers, centered and .75
-inches from the bottom of the page and make it start at the correct page
-number rather than the 4321 in the example.  To do this find the line (around
-line 23)  
-\begin{verbatim}
-%\ifthreedvfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
-\end{verbatim}
-where the number 4321 is your assigned starting page.
-
-Make sure the first page is numbered by commenting out the first page being
-empty on line 47
-\begin{verbatim}
-%\thispagestyle{empty}
-\end{verbatim}
+All printed material, including text, illustrations, and charts, must be
+kept within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches
+(22.54 cm) high.
 

### 2016-06-21 paper.tex
cm

@@
 
-\usepackage{3dv-2015authorkit/latex/3dv}
+\usepackage{3dv2016authorkit/latex/3dv}
 \usepackage{times}
@@
 % Include other packages here, before hyperref.
+%\usepackage{multicol}
+\usepackage{url}
 
@@
 % run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
 
@@
 \ifthreedvfinal\pagestyle{empty}\fi
+\setcounter{page}{4321}
 \begin{document}
@@
 
-%\author{Thomas S{\o}lund\\
-%Institution1\\
-%Institution1 address\\
-%{\tt\small thso@dti.dk}
-% For a paper whose authors are all at the same institution,
+\author{Thomas S{\o}lund\\
+Danish Technological Institute\\
+DK-5230 Odense M, Denmark\\
+{\tt\small thso@dti.dk}
+%For a paper whose authors are all at the same institution,
 % omit the following lines up until the closing ``}''.
@@
 % To save space, use either the email address or home page, not both
-%\and
-%Anders Glent Buch, Norbert Kr\"u{}ger\\
-%M\ae{}rsk Mc-Kinney M\o{}ller Institute,\\
-%University of Southern Denmark,\\
-%DK-5230 Odense, Denmark \\
-%{\tt\small anbu,norbert@mmmi.sdu.dk}
-%\and
-%Knut Conradsen, Henrik Aanæs\\
-%Department of Applied Mathematics\\ and Computer Science,\\ 
-%Technical University of Denmark\\
-%DK-2800 Kgs. Lyngby, Denmark\\
-%{\tt\small knco,aanes@dtu.dk}
-%}
+\and
+Anders Glent Buch, Norbert Kr\"u{}ger\\
+M\ae{}rsk Mc-Kinney M\o{}ller Institute,\\
+University of Southern Denmark,\\
+DK-5230 Odense, Denmark \\
+{\tt\small anbu,norbert@mmmi.sdu.dk}
+\and
+Henrik Aan\ae s\\ %Knut Conradsen, 
+Department of Applied Mathematics\\ and Computer Science,\\ 
+Technical University of Denmark\\
+DK-2800 Kgs. Lyngby, Denmark\\
+{\tt\small aanes@dtu.dk} %knco,
+}
 
@@
 \begin{abstract}
+  This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
+This is dummy text.
 To be written...........
@@
 %%%%%%%%% BODY TEXT
-\section{Introduction}
+
+%%%%%%%%%%Page limits = 8 exclusive references
+%Intro and related work -> 2.5 page
+%Experiantal design -> 1 page
+%Benchmark -> 1 page
+%Evaluation/results -> 3 pages
+% conclusion/discussion -> 1/2 page
+\section{Introduction} %Hvad, hvorfor, hvordan
 The ability to recognise objects in range images is a fundamental research area in computer vision with many different application areas.
@@
 Applications areas such as robotic assembly, bin-picking, mobile manipulation, biometric analysis, tracking and intelligent surveillance all benefits from 3D data for recognizing and localizing objects.
-Mainly, because the third dimension are explicit given and not inferred as known from 2D object recognition and pose estimation.
-In the last decades a huge effort in 2D object recognition and classification has been going on, where methods have been evaluated on large-scale dataset like the PASCAL Visual Object Challenge (VOC) \cite{Everingham2014}, ImageNet \cite{Imagenet2009}.
-The ability to evaluate on a large-scale dataset has proven valuable in the future algorithm development after the release of the PASCAL VOC and ImageNet datasets \cite{Everingham2014}.
-In 3D object recognition and pose estimation there still lacks a large-scale dataset in order to evaluate algorithms.
-Until today 3D object recognition and pose estimations has been evaluated at a couple of smaller datasets namely the UWA \cite{Mian2006}, Queens \cite{Taati2007}, Bologna \cite{Salti2014},\cite{Tombari2010}, Vienna Kinect\cite{Aldoma2012}, TUM \cite{Rodola2013}, TUM-LineMod\cite{Hinterstoisser2012}, BigBird\cite{BigBIRD} and RGB-D dataset version 1 \& 2\cite{Lai2011}, \cite{Lai2014}.
-In this work we present a evaluation of local shape features and present a new large-scale dataset consisting of 50 objects and 300 scenes.
-The new dataset is recorded systematically using a setup with a industrial robot, a structured light sensor and a Kinect V2 sensor, which records data from 11 different view points.
-Each scene consists of 10 objects  automatic take with two different sensors, which results in a dataset with around 66000 unique object poses.
+Mainly, because the third dimension are explicit given and not inferred as known from 2D object pose estimation.
+In the last decades a huge effort in 2D object recognition and classification has been going on, where methods have been evaluated on large-scale dataset like the PASCAL Visual Object Challenge (VOC) \cite{Everingham2014} and ImageNet \cite{Imagenet2009}.
+The ability to evaluate algorithms with a large-scale dataset has proven valuable in the future algorithm development after the release of the PASCAL VOC and ImageNet datasets \cite{Everingham2014}.
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.8\linewidth, height= 0.8\linewidth, keepaspectratio]{img/scenes/scene_000.pdf}
+\caption{Example of a scene}
+\label{fig:scene}
+\end{figure}
+In 3D object recognition and pose estimation there still is a need for a large-scale dataset that consistes of 3D querie models $Q_n$, 3D target scenes $S_t$ and ground truth poses $T_{gt}$ for each object in each scene, in order to be able to evaluate 3D object recognition algorithms better.
+Until today 3D object recognition has been evaluated at up to eight smaller datasets \cite{Guo2015}, include in the UWA \cite{Mian2006},\cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2007} and Bologna \cite{Salti2014},\cite{Tombari2010} dataset.
+Other, smaller dataset like the Vienna Kinect\cite{Aldoma2012}, TUM \cite{Rodola2013}, TUM-LineMod\cite{Hinterstoisser2012}, BigBird\cite{BigBIRD} and RGB-D dataset version 1 \& 2\cite{Lai2011}, \cite{Lai2014} have been proposed.
+Common for all dataset are that the amount of scenes and/or models are limited.\\
+%\begin{multicols}{3}
+\begin{table*}[ht]
+\label{tab:datasets}
+\centering % Center table
+         \begin{tabular}{p{4.2cm} p{0.3cm} p{1.2cm} p{1.5cm} p{1.55cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm}}
+                  %%  & \multicolumn{2}{c}{Data Size} & \multicolumn{4}{c}{Models} & \multicolumn{2}{c}{Scene} & \multicolumn{5}{c}{Ground truth} & he \\
+                  %%  \hline
+             & {$M_q$} & {$S_t$} &  Sensor & {$M_q$} in {$S_t$} & \rotatebox{90}{$M_q$ normals} & \rotatebox{90}{$M_q$ color } & \rotatebox{90}{$M_q$ mesh } & \rotatebox{90}{$S_t$ normals } & \rotatebox{90}{$S_t$ color } & \rotatebox{90}{$S_t$ mesh} & \rotatebox{90}{Full 6D pose} & \rotatebox{90}{Occlusion} & \rotatebox{90}{Clutter} & \rotatebox{90}{[R]/[S]}\\
+            \hline
+            \hline
+             UWA \cite{Mian2006}, \cite{Mian2010}  & 5 & 50 & LIDAR & (5)/(5) & \checkmark & \% & \checkmark & \checkmark & \%  & \checkmark & \checkmark  & \checkmark & \% & R\\
+             \hline
+             Queens Lidar  \cite{Taati2011}, \cite{Taati2007}  & 5 & 80 & LIDAR & (1-5)/(1-5) & \checkmark & \% & \checkmark & \% & \%  & 0 & \checkmark & \% & \% & R\\
+             \hline
+             Queens Stereo  \cite{Taati2011}, \cite{Taati2007}  & 5 & 100 & Stereo & (3)/(3)   & \checkmark & \% & \checkmark & \% & \%  & 0 & \checkmark & \% & \% & R\\
+             \hline
+             Bologna 1\&2 \cite{Salti2014}, \cite{Tombari2010} & 6 & 45 & LIDAR & (3-5)/(3-5) & \checkmark & \% & \checkmark & \checkmark & \% & \checkmark & \checkmark & \% & \% & S \\
+			 \hline              
+             Bologna 3 \cite{Salti2014}, \cite{Tombari2010} & 8 & 15 & Spacetime & (2)/(5-6) & \checkmark & \checkmark & \% & \checkmark & \checkmark & \checkmark & \checkmark & \% & \% & R\\
+             \hline
+             Bologna 4 \cite{Salti2014}, \cite{Tombari2010} & 8 & 16 & Spacetime & (2)/(6) & \checkmark & \checkmark & \% & \checkmark & \checkmark & \checkmark & \checkmark & \% & \% & R\\
+             \hline
+             Bologna 5 \cite{Salti2014}, \cite{Tombari2010} & 6 & 16 & Kinect V1 & (2-4)/(5-9) & \checkmark & \checkmark & \% & \checkmark & \checkmark & \checkmark & \checkmark & \% & \% & R \\
+             \hline
+             Vienna Kinect \cite{Aldoma2012} & 35 & 50 & Kinect V1 & 0 & \checkmark & \% & \checkmark & \% & \checkmark & 0 & \checkmark & \% & \% & R\\
+             \hline
+             RGB-D Scenes V1 \cite{Lai2011}, \cite{Lai2012} & 5 & 8 videos & Kinect V1 & (0)/ & \% & \% & \%  & \% & \checkmark  & \% & \% & \% & \% & R\\
+			 \hline             
+             RGB-D Scenes V2 \cite{Lai2014} & 9 & 14 & Kinect V1 & (0)/ & \% & \% & \% & \% & \checkmark & \% & \% & \% & \% & R\\
+             \hline
+             T{\"U}M \cite{Rodola2013} & 20 & 150 & kinect & (3-5)/(3-5) & \checkmark  & \%  & \checkmark  & \checkmark & \% & \checkmark & \checkmark & \checkmark & \checkmark & S\\
+             \hline
+             Willow \cite{Willow} & 35 & 177 & kinect & 0 & \checkmark  & \checkmark  & \checkmark  & \% & \checkmark & 0 & \% & \% & \% & R\\
+             \hline
+            % B3DO \cite{Janoch2011}  & 0 & 849 & kinect & 0 & \%  & \%  & \%  & \% & \checkmark & \% & \% & \% & R\\
+            % \hline
+             ECCV12 \cite{Aldoma2012}  & 35 & 50 & Kinect V1 & (3-7)/(3-7) & \%  & \checkmark  & \checkmark  & \% & \% & \% & \checkmark & \% & \% & R\\
+             \hline
+              Alicante \cite{Garcia-Garcia2016}  & 30 & 50 & Kinect V2 & (0)/(0) & \%  & \checkmark  & \checkmark  & \% & \% & 0 & \checkmark & \% & \% & R\\
+             \hline
+             \hline
+             \textbf{Our SL dataset}  & \textbf{50} & \textbf{3300} & SL & (10)/(10) & \checkmark  & \checkmark  & \checkmark  & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark & R\\
+             \hline
+             \textbf{Our Kinect dataset}  & \textbf{50} & \textbf{3300} & Kinect V2 & (10)/(10) & \checkmark  & \checkmark  & \checkmark  & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark & R\\
+             \hline 
+        \end{tabular}
+%        \captionof{table}{Existing datasets for 3D object recognition and pose estimation}% Add 'table' caption
+        \label{dataset_overview}
+
+\caption{Comparison of existing datasets for 3D object recognition with the presented datasets.
+{$M_q$} is the amount of different models in the dataset and {$S_t$} is the amount of scenes.[R]/[S] indicates whether the dataset is synthetic or acquired in real world.
+}
+\end{table*}
+%\end{multicols}
+In this work we present a new large-scale dataset consisting of 50 objects and 3300 scenes.
+The new dataset is recorded systematically in an environment without ambient light and with controlled illumination.
+The system includes a industrial robot in a dark chamber, a high precision structured light scanner and a Kinect V2 sensor, which records data from 11 different view points.
+Each scene consists of 10 objects automatic taken with the two different sensors, which results in a dataset with around 66000 unique object poses.
+With 11 different views of the same scene our dataset is especially suited for studying the effect of view point changes in 3D object recognition.
+Our 50 object models are scanned in a similar dark chamber with a high precision structured scanner and a rotation table.
+With this setup we are able to scan objects with an accuracy down to XX microns.
+We use the dataset to evaluate state of the art local shape features in a 3D object recognition pipeline.
+In Table \ref{tab:datasets} a summery of the features of ours and state of the art dataset are presented.\\
+Why do the 3D Object recognition community needs another dataset?
+Current proposed dataset is limited in the number of objects/scenes and the objects included in the datasets are mostly geometrical ideal objects.
+With geometrical ideal objects we refers to mostly concave objects that are rich of geometrical features like the UWA-chef model \cite{Mian2006},\cite{Mian2010}, the bologna-Armadillo \cite{Salti2014},\cite{Tombari2010} and the Queens-BigBird \cite{Taati2007},\cite{Taati2007}.
+With our dataset we introduce not only ideal concave objects, but flat, cylindrical, feature-rich and feature-poor concave and convex objects.
+Our objects are a combination of lab-objects and industrial objects which are selected from companies that wants to pick these objects from boxes or bins with a robot.\\
+This paper is structured as follows: In Section \ref{sec:related_work} related datasets and local feature descriptors are presented.
+Section \ref{sec:exp_design} details our experimental design followed by Section \ref{sec:benchmark} which presents our benchmarking methodology.
+In Section \ref{sec:evaluation} the results are given followed by a discussion and conclusion in Section \ref{sec:conclusion}.
+%-------------------------------------------------------------------------
+	\section{Related work} \label{sec:related_work}
+%We are not considering learning approaches
+\textbf{3D Object Recognition datasets:}\\
+
+\textbf{Local feature descriptors:}\\
+During the last three decade, a vast number of different 3D local feature descriptors have been proposed including SPLASH \cite{Stein1992}, Spin Image (SI) \cite{Johnson1999}, 3DSC \cite{Frome2004}, LSP \cite{ChenBhanu2004}, 3D Tensor \cite{Mian2006}, THRIFT \cite{Flint2007}, MESH-HOG \cite{Zaharescu2009}, ISS \cite{Zhong2009}, USC \cite{usc2010}, PFH \cite{Rusu2008}, FPFH \cite{Fpfh2009}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015}, Tri-Spin-Image (TriSI)\cite{Guo2015}.
+The descriptors find usages in applications such as 3D object categorization, recognition, retrial, analysis, registration and reconstruction among others.
+Designing descriptors which are distinctive and robust to occlusion and noise are still and ongoing research topic.
+Recent studies has shown that the proposed features are not generalizing well over many types of geometry classes, \cite{Guo2015},\cite{Buch2016}.
+The studies proved one of the main issue in 3D object recognition today, namely the fact that there exist no local shape feature that describes the geometry well in many different object classes, e.g.
+flat, rotational symmetrical and geometrical feature rich objects.
+What feature(s) to use are still dependant of the object geometry.
+These studies poses a relevant research question, are the local feature descriptors not descriptiveness enough to generalize over different object classes or are the evaluation data to limited?
+The evaluation dataset there are used for the evaluation in general and in \cite{Guo2015},\cite{Buch2016}, consists mainly of objects with many descriptive and distinctive geometrical features.
+In this work we try to answer this fundamental question by creating the data foundation to evaluate the performance of each local feature descriptors by applying statistic.
+
+Local feature descriptor aims at computing a distinctive and robust N-dimensional feature vector around a point, by considering the k-neighbour points in euclidean space.
+The radius of the K-Nearest Neighbour search (KNN), the support radius is often one of the critical parameters in the pipeline.
+Local feature descriptors are often split into tow different categories, spatial and geometrical histograms \cite{Guo2015}.
+Global feature descriptors, typical computes a descriptors by considering the spatial and/or geometrical relations between two or more local feature descriptors on a 3D geometry.
+
+Local shape features can be split into two different categories, spatial and geometrical histograms \cite{Guo2015}. 
+Early work by Stein and Medioni \cite{Stein1992} used a combination of edges and small surfaces patches for 3D matching in range images.
+Later Johnson  and Albert introduced Spin Images \cite{Johnson1999}
+
+Spin Images \cite{Johnson1999}\\
+Froome \etal \cite{Frome2004} presented a local descriptor 3D shape context.
+%USC \cite{usc2010}\\
+
+%PFH \cite{Rusu2008}
+%FPFH \cite{Fpfh2009}\\
+%ECSAD \cite{Ecsad2015}\\
+%ROPS \cite{Guo2013}\\
+%SHOT \cite{Salti2014}\\
+%NDHIST\\
+%PPF \cite{Drost2010}\\
+%SHOT \cite{Tombari2010}\\
+
+Recently, a couple of benchmarks of local feature descriptors has been presented. Guo \etal \cite{Guo2015} presented a comprehensive comparison of most common local feature descriptors. The 
+Feature Fusion \cite{Buch2016}\\
+Feature comparision Yulan et.al. \cite{Guo2015}
 
@@
 %RGB-D Dataset V2 \cite{Lai2014}\\ 
+%------------------------------------------------------------------------
+\section{Experimental design} \label{sec:exp_design}
+%Describe the object scanning process
+\subsection{Object model scanning}
+Our object models are scanned with a high precision structured light setup consisting of two industrial cameras (Point Grey Research GS3-U3-91S6C-C) and
+a high resolution DLP projector (LG PF80G) mounted on a rigid aluminium frame.
+In addition, a high precision turntable (Newmark Systems RT-5) is used in order to provide automatic rotation of the object.
+Each of the 50 objects are incremental scanned with a rotation of 20 degrees.
+All individual scan views are reconstructed by the Line shifting algorithm \cite{Guehring2000} which results in accurate and dense point cloud of the objects.
+Eleven temporal binary gray code patterns are projected followed by eight line shifting patterns.
+The point resolution of the scanner is XX.
+Once a single view of the model are scanned, noisy outliers of the measurement are manual removed and surface normals are estimated to ensure consistent normals.
+All 18 views are registered with Iterative Closest Point (ICP) and the object frame are computed by principal component analysis.
+All models are sampled with a Poisson disk sampling algorithm and triangulated with the poisson reconstruction algorithm \cite{Kazhdan2006} with an octree depth=14, Solver divide = x and xx = xx.
+We use the PCL implementation \cite{RusuCousins2011}.
+All models are provided as coloured point clouds and triangular meshes, all in the $.ply$ format, see Figure \ref{fig:objects}.
+Note that the modelling setup is not radiometrical calibrated.
+\begin{figure}[ht]
+\centering
+\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/objects/objects.pdf}
+\caption{Four of the fifty scanned and triangulated object models}
+\label{fig:objects}
+\end{figure}
+%Describe setup for scene aqusition
+\subsection{Scene scanning} 
+For the data collection we use the robot depicted at Figure \ref{fig:robot}.
+The robot is equipped with two PointGray Grasshopper3 GS3-U391S6C-C USB3 color cameras with resolution of 9.1 Mp, a Wintech Pro4500 projector with a resolution of 1140x912 pixels and a Kinect One sensor.
+The sensor cluster is mounted in the robot tool.
+The sensor modalities are selected by two reasons.
+First, the structured light system (SL) ensure a high precision that is XX times better than the Kinect thus we are able to provide accurate ground truth pose data for each object in the scene down to a precision of xx mm.
+Second, Time-of-Flight sensors like the Kinect One sensor are popular sensors in many research areas such as robotic manipulation, 3D semantic mapping, people detection and consumer products thus we wanted to support the future development of 3D object recognition systems and algorithms by including the sensor in the dataset.
+The Robot setup is constructed as a radiometric "dead" which gives a scene representation with zero ambient light.
+All the scene illumination is controlled in the recording process.
+The sensor cluster is calibrated with a automatic calibration procedure which includes a stereo calibration of the SL sensor using \verb|OpenCV|\footnote{\url{http://opencv.org/}} and a intrinsic calibration of the Kinect using the \verb|iai_kinect2|\footnote{\url{https://github.com/code-iai/iai_kinect2}} software package.
+The Kinect calibration ensure a proper registration of the RGB values at each 3D point.
+An automatic hand eye calibration \cite{DornaikaHoraud1998} is conducted in order to align the Kinect and the SL scans in the world frame.
+The world frame is the robot base frame.
+%Describe recording procedure
+Each scene are scanned from 11 different views with both the structured line scanner (SL) and the Kinect such that each physical scene results in 11 SL and 11 Kinect scenes, 22 scenes in total.
+During the SL scanning process the chamber is completlty dark in order to increase the signal-to-noise ration of the scan.
+When the Kinect scene are depicted a two diffuse light projectors are automatical turned on to depict the kinect colors.
+The level of diffuse scene ligth are empirical dertermined such that the kinect RGB camera not oversaturating.
+The structured light scans are reconstructed with the Line shifting algorithm \cite{Guehring2000} with ten temporal pattern levels.
+The views are distributed equally on a quarter sphere around the scene, such that each scene is depicted from - 90 to 90 degrees horizontally and 0 to 45 degree vertically.
+In order to reproduce the results we store raw Portable Network Graphics images in full resolution (9.1 MP).
+De-bayering, white balance, image rectification, pattern decoding and point cloud reconstruction are a off line process.
+
+%Meshing of the scenes + normal estimation
+%\begin{figure}[ht]
+%\centering
+%\includegraphics[width=1.0\linewidth, height= 0.7\linewidth]{img/dummy.pdf}
+%\caption{Scan of the full scene with view frames}
+%\label{fig:scene}
+%\end{figure}
+%A Note on ground truth
+\subsection{Ground Truth 6D pose}
+For each of the ~3300 scenes the 6D ground truth pose, occlusion and clutter estimates for each object are provided.
+We estimate the occlusion from Equation \ref{eq:occlusion} and clutter from Equation \ref{eq:clutter} by counting the number of points at the object model which squared euclidean distance to a scene point is less than two times the resolution.
+Both the object model and the scene are sampled to ensure equal point distance.
+\begin{equation}
+Occlusion = 1 - \frac{visible object points}{total object points} 
+\label{eq:occlusion}
+\end{equation}
+\begin{equation}
+Clutter = 1 - \frac{visible object points}{total scene points}
+\label{eq:clutter}
+\end{equation}
+Accurate ground true poses are ensure by registration of the individual SL scans into one full scene model in world frame which covers the geometric structures of all the models in the particular scene, see Figure \ref{fig:scene}.
+The hand/eye calibration procedure computes the transformation from each sensor frame to the robot flange such that every transformation is known in the system.
+With all transformation known, it is trivial to align the kinect scans with full SL scene by applying the transformation $T_{kinect2SL}$ followed by fine ICP registration $T_{ICP}$ on the full resolution SL scene.
+All ~300 combined scenes are manual annotated by selecting four identical points for each model and the scene followed by an estimation of the rigid transform.
+An iterative ICP, which incremental decrease the max allowed correspondence euclidean distance on the full resolution cloud ensures the ground truth pose.
+The individual ground truth poses in each sensor view $T{s_n}$ are generate by transforming ground truth pose from the world frame $T_{w}$ to each of the individual sensor frames $T{s_n}$ by applying the equation $T^{w}_{s_n} = $.
+This methodology guarantees accurate pose in $T{s_n}$ independent of the amount of occlusion.
+Even in views with limited number of scene point of an object the ground truth pose is accurate.
+Moreover, we align each Kinect scans in $T{s_n}$ to the SL scan by applying the transform $T=$ which gives an accurate ground truth pose for the noisy Kinect data based on dense and accurate SL data.
+
+%We provide 6D ground truth poses with RMS error for the final ICP registration. In this way we can guarantee that the overall accuracy of all ground truth poses is within xx mm. 
+%Combine the 11 views. The different scans are then aligned with respect to scan number zero by applying
+%These view points ensure a good coverage of the scene and provide the needed geometric structure of each object to reliable compute ground truth. 
+%alignment two frame 0. alignment of kinect scene and transformation back to the sensor frame.
 
 %-------------------------------------------------------------------------
-\section{Related work}
-%We are not considering learning approaches
-\textbf{Local Shape features:}\\
+\section{Benchmark}\label{sec:benchmark}
+This section describes the experimental protocol defined for the evaluation of the dataset.
+The evaluation is divide into two parts; feature descriptivness and recognition rate.
+The selected local feature descriptors for our evaluation includes; Spin Image (SI) \cite{Johnson1999}, 3DSC \cite{Frome2004}, PFH \cite{Rusu2008}, FPFH \cite{Fpfh2009}, USC \cite{usc2010}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015} and NDHIST \cite{Buch2016}.
+The features are selected based on implementation availability and results from previous studies on feature descriptor benchmarking \cite{Guo2015}, \cite{Buch2016}.
+Precision-Recall Curves (PRC) are used to evaluate the descriptiveness and accuracy of a feature descriptor.
+The
 
-Spin Images \cite{Johnson1999}\\
-Froome \etal \cite{Frome2004} presented a local descriptor 3D shape context.
-USC \cite{usc2010}\\
+"For each target model, the seed points of each query model are placed in the scene using the ground truth pose, and the target seed points are now described.
+We use voxel gird for sampling \cite{RusuCousins2011} to get uniform point distance.
+Following the seed point sampling, each seed point are described by the nine feature descriptors.
 
-FPFH \cite{Fpfh2009}\\
-ESAC \cite{Ecsad2015}\\
-ROPS \cite{Guo2013}\\
-SHOT \cite{Salti2014}\\
-NDHIST\\
-PPF \cite{Drost2010}\\
-SHOT \cite{Tombari2010}\\
+"In general the matching accuracy of a descriptor is expected to increase with increasing support radius, except in cases where occlusion and clutter are present." For fair comparison individually tuned support radii for each descriptors are used; SI($xx$), 3DSC($xx$), PFH($xx$), FPFH($xx$), USC($xx$), SHOT($xx$), ROPS($xx$), ECSAD($xx$), NDHIST($xx$).
 
-Feature Fusion \cite{Buch2016}\\
-Feature comparision Yulan et.al. \cite{Guo2015}
+For each query and target we add three levels of gaussian noise to the vertex position
+%-------------------------------------------------------------------------
+\section{Evaluation}\label{sec:evaluation}
 
-%------------------------------------------------------------------------
-%\section{Experimental design}
+\begin{figure*}[htp]
+\centering
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[width=1.0\linewidth, height= 0.7\linewidth, keepaspectratio]{img/PRC_1.pdf} 
+\caption{Noise level 1 for STL dataset}\label{fig:stl_n1}
+\end{minipage}\qquad
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
+\caption{Noise level 2 for STL dataset}\label{fig:stl_n2}
+\end{minipage}
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
+\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
+\end{minipage}
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf} 
+\caption{Decimination level 1 for STL dataset}\label{fig:stl_d1}
+\end{minipage}\qquad
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
+\caption{Decimination level 2 for STL dataset}\label{fig:stl_d2}
+\end{minipage}
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
+\caption{Decimination level 3 for STL dataset}\label{fig:stl_d3}
+\end{minipage}
+\end{figure*}
+
+\begin{figure*}[htp]
+\centering
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf} 
+\caption{Noise level 1 for Kinect dataset}\label{fig:kinect_n1}
+\end{minipage}\qquad
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
+\caption{Noise level 2 for Kinect dataset}\label{fig:kinect_n2}
+\end{minipage}
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
+\caption{Noise level 3 for Kinect dataset}\label{fig:kinect_n3}
+\end{minipage}
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf} 
+\caption{Decimination level 1 for Kinect dataset}\label{fig:kinect_d1}
+\end{minipage}\qquad
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
+\caption{Decimination level 2 for Kinect dataset}\label{fig:kinect_d2}
+\end{minipage}
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
+\caption{Decimination level 3 for Kinect dataset}\label{fig:kinect_d3}
+\end{minipage}
+\end{figure*}
 
 %-------------------------------------------------------------------------
-%\section{Benchmark}
-
-%-------------------------------------------------------------------------
-%\section{Evaluation}
-
-%-------------------------------------------------------------------------
-%\section{Discussion}
-
-%-------------------------------------------------------------------------
-%\section{Conclusion}
+\section{Discussion \& Conclusion}\label{sec:conclusion}
 
@@
 {\small
-\bibliographystyle{3dv-2015authorkit/latex/ieee}
+\bibliographystyle{3dv2016authorkit/latex/ieee}
 \bibliography{bib}
 }
+
 \end{document}

### 2016-06-30 paper.tex
experimental design

@@
 
-\def\threedvPaperID{****} % *** Enter the 3DV Paper ID here
+\def\threedvPaperID{4} % *** Enter the 3DV Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
              \hline
-             Bologna 1\&2 \cite{Salti2014}, \cite{Tombari2010} & 6 & 45 & LIDAR & (3-5)/(3-5) & \checkmark & \% & \checkmark & \checkmark & \% & \checkmark & \checkmark & \% & \% & S \\
+             Bologna 1\&2 \cite{Salti2014}, \cite{Tombari2010} & 6 & 45 & - & (3-5)/(3-5) & \checkmark & \% & \checkmark & \checkmark & \% & \checkmark & \checkmark & \% & \% & S \\
 			 \hline              
@@
              \hline
-             T{\"U}M \cite{Rodola2013} & 20 & 150 & kinect & (3-5)/(3-5) & \checkmark  & \%  & \checkmark  & \checkmark & \% & \checkmark & \checkmark & \checkmark & \checkmark & S\\
+             T{\"U}M \cite{Rodola2013} & 20 & 150 & - & (3-5)/(3-5) & \checkmark  & \%  & \checkmark  & \checkmark & \% & \checkmark & \checkmark & \checkmark & \checkmark & S\\
              \hline
-             Willow \cite{Willow} & 35 & 177 & kinect & 0 & \checkmark  & \checkmark  & \checkmark  & \% & \checkmark & 0 & \% & \% & \% & R\\
+             Willow \cite{Willow} & 35 & 177 & Kinect V1 & 0 & \checkmark  & \checkmark  & \checkmark  & \% & \checkmark & 0 & \% & \% & \% & R\\
              \hline
@@
 \textbf{3D Object Recognition datasets:}\\
+The last 10 years a few 3D object recognition datasets have been published.
+Mainly in conjunction with algorithms for local feature description \cite{Mian2006},\cite{Taati2007},\cite{Taati2011},\cite{Tombari2010},\cite{Salti2014}, correspondence matching and rejection \cite{Rodola2013}, pose hypothesis verification \cite{Aldoma2012} and 3D keypoint detection \cite{Mian2010}.
+Common for all existing dataset are the limited number of 3D object models and scenes.
+A comparison of the different datasets are presented in Table \ref{tab:datasets}.
+The most common used datasets are the UWA  \cite{Mian2006}, \cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2011} and the Bologna \cite{Salti2014}, \cite{Tombari2010}.
+These datasets are widely used in performance evaluations of  local feature descriptors \cite{Guo2015}, \cite{Buch2016}, keypoint detectors \cite{Salti2011} and surveys \cite{Guo2014}, \cite{FilipeAlexandre2014}.
+The main problem of all the datasets are; size, variety of objects and occlusion/clutter estimates.
+The recent comparison studies \cite{Guo2015}, \cite{Buch2016} revival that the data for evaluation are not good enough to scientific distinguish results.
+The studies exactly showed that one local feature descriptor preformed very good for one dataset but fail in other datasets.
+The reason could be twofold; the local feature descriptors are not generalizing well and/or the evaluation data is too limited.
+This work tries to answer this question.\\
 
 \textbf{Local feature descriptors:}\\
-During the last three decade, a vast number of different 3D local feature descriptors have been proposed including SPLASH \cite{Stein1992}, Spin Image (SI) \cite{Johnson1999}, 3DSC \cite{Frome2004}, LSP \cite{ChenBhanu2004}, 3D Tensor \cite{Mian2006}, THRIFT \cite{Flint2007}, MESH-HOG \cite{Zaharescu2009}, ISS \cite{Zhong2009}, USC \cite{usc2010}, PFH \cite{Rusu2008}, FPFH \cite{Fpfh2009}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015}, Tri-Spin-Image (TriSI)\cite{Guo2015}.
+{\color{red} AGB will you write this. Length around 1 colum}
+During the last three decade, a vast number of different 3D local feature descriptors have been proposed including SPLASH \cite{Stein1992}, Spin Image (SI) \cite{Johnson1999}, 3D Shape Contex (3DSC) \cite{Frome2004}, LSP \cite{ChenBhanu2004}, 3D Tensor \cite{Mian2006}, THRIFT \cite{Flint2007}, MESH-HOG \cite{Zaharescu2009}, ISS \cite{Zhong2009}, Unique shape context (USC) \cite{usc2010}, Point Feature Histogram (PFH)\cite{Rusu2008}, Fast Point Feature Histogram (FPFH) \cite{Fpfh2009}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015}, Tri-Spin-Image (TriSI)\cite{Guo2015}.
 The descriptors find usages in applications such as 3D object categorization, recognition, retrial, analysis, registration and reconstruction among others.
@@
 Second, Time-of-Flight sensors like the Kinect One sensor are popular sensors in many research areas such as robotic manipulation, 3D semantic mapping, people detection and consumer products thus we wanted to support the future development of 3D object recognition systems and algorithms by including the sensor in the dataset.
+\begin{figure}[ht]
+\centering
+\includegraphics[width=1.0\linewidth, height= 0.7\linewidth]{Robot.pdf}
+\caption{Scan of the full scene with view frames}
+\label{fig:robot}
+\end{figure}
 The Robot setup is constructed as a radiometric "dead" which gives a scene representation with zero ambient light.
@@
 %Meshing of the scenes + normal estimation
-%\begin{figure}[ht]
-%\centering
-%\includegraphics[width=1.0\linewidth, height= 0.7\linewidth]{img/dummy.pdf}
-%\caption{Scan of the full scene with view frames}
-%\label{fig:scene}
-%\end{figure}
+
 %A Note on ground truth
@@
 \section{Benchmark}\label{sec:benchmark}
-This section describes the experimental protocol defined for the evaluation of the dataset.
-The evaluation is divide into two parts; feature descriptivness and recognition rate.
+This section outlines the experimental protocol defined to evaluate of the dataset.
+The protocol are inspired by the one used by Salti \etal \cite{Salti2014}.
+The evaluation is divide into two parts; feature matching and recognition.
 The selected local feature descriptors for our evaluation includes; Spin Image (SI) \cite{Johnson1999}, 3DSC \cite{Frome2004}, PFH \cite{Rusu2008}, FPFH \cite{Fpfh2009}, USC \cite{usc2010}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015} and NDHIST \cite{Buch2016}.
-The features are selected based on implementation availability and results from previous studies on feature descriptor benchmarking \cite{Guo2015}, \cite{Buch2016}.
-Precision-Recall Curves (PRC) are used to evaluate the descriptiveness and accuracy of a feature descriptor.
-The
+The features are selected based on implementation availability and results from previous studies on feature descriptor benchmarking \cite{Guo2015},\cite{Buch2016}.
+\subsection{Feature Matching}
+The descriptiveness and accuracy of a feature descriptor are measured with Precision-Recall and presented as 1-Precision vs.
+Recall Cruves (PRC).
+First we sample both the query model and the target scene with a voxel grid sampling \cite{RusuCousins2011} which results in equal point distance.
+The Voxel size are tune to give approximately XXXX seed points per.
+object in both the query and target.
+The target seed points are found by transforming the query seed into the sampled scene using the ground truth pose and selecting scene points by a nearest neighbour search with a distance threshold.
+A feature descriptor for each seed points for the query and target mesh are computed.
+For fair comparison individually tuned support radii for each descriptors are used; SI($xx$), 3DSC($xx$), PFH($xx$), FPFH($xx$), USC($xx$), SHOT($xx$), ROPS($xx$), ECSAD($xx$), NDHIST($xx$).
+Upon feature computation the underlying meshes are utilized in a 0.xx \% decimated version.
+The level of decimation are empirical determined to the level with best overall matching results for all features.
+During decimation the normal orientation are re-computed for each vertex by the area weighted mean of the mesh triangle \cite{Thurmer1998}.
+In order to resolve the exact number of correct feature matches, an brute-force linear kd tree search are used with the ${L_2}$ distance function.
+Once all matches for all queries are computed they are ranked and sorted according to the ${L_2}$ distance in one array.
+The correct matches are found by traversing the array of matches and count the number of matches that are spatial close, determined by a distance threshold.
+The PRC curves are presented in Section \ref{sec:evaluation} where precision refers to the number of correct matches compared to the total number of matches.
+Recall refers to to the number correct matches compared to the total amount of possible matches (i.e.
+feature seed points found in the target).
+In addition to PRC curves the maximum F1 score are given as a single quantitative measure of the overall accuracy.
+The max F1 score are computed as the maximun harmonic mean over all (P,R) and the formula is presented in Equation \ref{eq::maxf1}.
+%Ratio of the nearest matching feature distance to that of the second nearest \cite{Buch2016}  
+\begin{equation}\label{eq::maxf1}
+max F_1 = {max}_{(P,R)} \left(2 \cdot \frac{P\cdot R}{P+R}\right)
+\end{equation}
+\subsection{Pose estimation}
+In this section the experimental protocol for the pose estimation experiments are presented.
+The sampling and seed point selection are identical with the feature matching benchmark presented except that we cannot use the ground truth pose for selecting target seed points.
+Instead, the target resolution are doubled, to quadruples the number of feature descriptors which increase the chance for describing the same feature.
+For increase the efficiency in the matching we now apply approximate nearest neighbour search to determine correspondences hypotheses instead of exact matching.
+Again, the ratio of the nearest and second nearest neighbours feature distance are used.
+A multiple randomized kd-trees with a bound of 512 checks and 4 trees are used as a good trade-off between accuracy and efficiency.
+Correspondences are ranked by ${L_2}$ distance which inputs potential feature correspondences to a hypothesis and test RANSAC algorithm.%ref to Muja and Lowe?
+During random sampling, three correspondences are sampled which is sufficient to generate a hypothesis pose.
+The hypothesis pose is tested by transforming the query point and counting the number of query points lie close to the target feature up to a tolerance given by the inlier threshold.
+The algorithm filters out false positives by setting a lower minimum of the number of inliers required to accept a pose hypothesis to {\color{red}5\%}.
+The the pose with the highest number of inliers are returned as the object pose.
+Our RANSAC implementation deviate from classic RANSAC, which treats all data points uniformly, by sampling correspondences by their quality score.
+The quality scores are given by the negative normalized ${L_2}$ distance ratio.
+The efficiency of the algorithm is further increased by discard the 50\% of the correspondences with the lowest quality score before running the RANSAC algorithm.
+Upon RANSAC completion the final pose are refined by {\color{red}50} ICP iterations on the query/target seed points and.
 
-"For each target model, the seed points of each query model are placed in the scene using the ground truth pose, and the target seed points are now described.
-We use voxel gird for sampling \cite{RusuCousins2011} to get uniform point distance.
-Following the seed point sampling, each seed point are described by the nine feature descriptors.
+Dertermine if the pose is correctly estimated we compare it with the ground true pose provide in the dataset
 
-"In general the matching accuracy of a descriptor is expected to increase with increasing support radius, except in cases where occlusion and clutter are present." For fair comparison individually tuned support radii for each descriptors are used; SI($xx$), 3DSC($xx$), PFH($xx$), FPFH($xx$), USC($xx$), SHOT($xx$), ROPS($xx$), ECSAD($xx$), NDHIST($xx$).
+\begin{equation}\label{eq::rot}
+arccos \left(\frac{trace(\textbf{R}^{T}\hat{\textbf{R}})-1}{2}\right) \leq 7.5^\circ
+\end{equation}
+\begin{equation}\label{eq::trans}
+||\textbf{t} - \hat{\textbf{t}} || \leq 0.01m
+\end{equation}
 
-For each query and target we add three levels of gaussian noise to the vertex position
+%For each query and target we add three levels of gaussian noise to the vertex position
 %-------------------------------------------------------------------------
 \section{Evaluation}\label{sec:evaluation}
+
+RANSAC iterations = xxxx and ICP = xxx 
+"In general the matching accuracy of a descriptor is expected to increase with increasing support radius, except in cases where occlusion and clutter are present." 
+% Figure:
+% 1 x PRC for STL scener
+% 1 x PRC for kinect scener
+% 3 x PRC for objekt grupper STL scener
+% 3 x PRC for objekt grupper Kinect scener
+% 1 x graf med emner på x aksen og max F1 eller AUC på y aksen for hver feature
+% 1 x tabel recognition rate
 
@@
 
+\begin{table}[ht]
+\centering
+\begin{tabular}{llllll}
+\hline
+\textbf{Feature} & \textbf{STL} & \textbf{Kinect} & \textbf{Gr. 1}  &\textbf{Gr. 2} &\textbf{Gr. 3} \\
+\hline
+ \textbf{\textit{ECSAD}}  & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
+ \textbf{\textit{FPFH}}   & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
+ \textbf{\textit{NDHIST}} & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
+ \textbf{\textit{ROPS}}   & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
+ \textbf{\textit{SHOT}}   & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
+ \textbf{\textit{SI}}     & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
+ \textbf{\textit{USC}}    & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
+ \textbf{\textit{PFH}}    & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
+ \textbf{\textit{3DSC}}   & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
+ \hline
+ \hline
+ \textbf{\textit{Mean ($\lambda$)}}   & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
+ \hline
+ \\
+\end{tabular}
+\caption{Overall recognition rates.
+\textbf{First column:} Features descriptors.
+\textbf{Second column:} Recognition rate for the full stl dataset.
+\textbf{Third column:} Recognition rate for the full kinect dataset.
+\textbf{Fourth column:} Recognition rate for group 1 object subset.
+\textbf{Fifth column:} Recognition rate for group 2 object subset.
+\textbf{Sixth column:} Recognition rate for group 2 object subset.}
+\label{tab:recognition}
+\end{table}
+
 %-------------------------------------------------------------------------

### 2016-06-30 paper.tex
Related

@@
 \centering % Center table
-         \begin{tabular}{p{4.2cm} p{0.3cm} p{1.2cm} p{1.5cm} p{1.55cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm}}
+         \begin{tabular}{p{3.5cm} p{0.3cm} p{1.2cm} p{1.5cm} p{1.55cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm}}
                   %%  & \multicolumn{2}{c}{Data Size} & \multicolumn{4}{c}{Models} & \multicolumn{2}{c}{Scene} & \multicolumn{5}{c}{Ground truth} & he \\
@@
 %-------------------------------------------------------------------------
-\section{Related work} \label{sec:related_work}
+\section{Related work}\label{sec:related_work}
 %We are not considering learning approaches
@@
 The reason could be twofold; the local feature descriptors are not generalizing well and/or the evaluation data is too limited.
-This work tries to answer this question.\\
+This work tries to answer this question.
+{\color{blue} Unclear last sentence.
+How?}\\
 
 \textbf{Local feature descriptors:}\\
-{\color{red} AGB will you write this. Length around 1 colum}
-During the last three decade, a vast number of different 3D local feature descriptors have been proposed including SPLASH \cite{Stein1992}, Spin Image (SI) \cite{Johnson1999}, 3D Shape Contex (3DSC) \cite{Frome2004}, LSP \cite{ChenBhanu2004}, 3D Tensor \cite{Mian2006}, THRIFT \cite{Flint2007}, MESH-HOG \cite{Zaharescu2009}, ISS \cite{Zhong2009}, Unique shape context (USC) \cite{usc2010}, Point Feature Histogram (PFH)\cite{Rusu2008}, Fast Point Feature Histogram (FPFH) \cite{Fpfh2009}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015}, Tri-Spin-Image (TriSI)\cite{Guo2015}.
-The descriptors find usages in applications such as 3D object categorization, recognition, retrial, analysis, registration and reconstruction among others.
-Designing descriptors which are distinctive and robust to occlusion and noise are still and ongoing research topic.
+{\color{red} AGB will you write this. Length around 1 colum} {\color{blue} Done.}
+During the last three decades, a vast number of different 3D local feature descriptors have been proposed including SPLASH \cite{Stein1992}, Spin Image (SI) \cite{Johnson1999}, 3D Shape Context (3DSC) \cite{Frome2004}, LSP \cite{ChenBhanu2004}, 3D Tensors \cite{Mian2006}, THRIFT \cite{Flint2007}, MESH-HOG \cite{Zaharescu2009}, ISS \cite{Zhong2009}, Unique shape context (USC) \cite{usc2010}, Point Feature Histogram (PFH) \cite{Rusu2008}, Fast Point Feature Histograms (FPFH) \cite{Fpfh2009}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015} and Tri-Spin-Image (TriSI)\cite{Guo2015}.
+The descriptors find usages in applications such as 3D object categorization, recognition, retrieval, analysis, registration and reconstruction among others.
+Designing descriptors which are distinctive and robust to occlusion and noise is still an ongoing research topic.
 Recent studies has shown that the proposed features are not generalizing well over many types of geometry classes, \cite{Guo2015},\cite{Buch2016}.
-The studies proved one of the main issue in 3D object recognition today, namely the fact that there exist no local shape feature that describes the geometry well in many different object classes, e.g.
-flat, rotational symmetrical and geometrical feature rich objects.
-What feature(s) to use are still dependant of the object geometry.
-These studies poses a relevant research question, are the local feature descriptors not descriptiveness enough to generalize over different object classes or are the evaluation data to limited?
-The evaluation dataset there are used for the evaluation in general and in \cite{Guo2015},\cite{Buch2016}, consists mainly of objects with many descriptive and distinctive geometrical features.
-In this work we try to answer this fundamental question by creating the data foundation to evaluate the performance of each local feature descriptors by applying statistic.
+The studies proved one of the main issue in 3D object recognition today, namely the fact that there exist no local shape feature that describes the geometry well over many different object classes, e.g.
+flat, rotational symmetrical and geometrically feature rich objects.
+What feature(s) to use are still dependent on the object geometry.
+These studies pose a relevant research question, are the local feature descriptors not descriptiveness enough to generalize over different object classes or are the data used for evaluation too limited?
+The evaluation datasets used for the evaluation in general and in \cite{Guo2015},\cite{Buch2016} consist mainly of objects with many descriptive and distinctive geometrical features.
+In this work we try to answer this fundamental question by creating a better data foundation and by evaluating the performance of each local feature descriptors by applying statistical analyses.
+{\color{blue} TS This last sentence I believe is not relevant anymore, since the statistical analysis are postponed?}
 
-Local feature descriptor aims at computing a distinctive and robust N-dimensional feature vector around a point, by considering the k-neighbour points in euclidean space.
-The radius of the K-Nearest Neighbour search (KNN), the support radius is often one of the critical parameters in the pipeline.
-Local feature descriptors are often split into tow different categories, spatial and geometrical histograms \cite{Guo2015}.
+Local feature descriptors aim at computing a distinctive and robust N-dimensional feature vector around a point, by considering the points in an Euclidean neighborhood.
+The support radius determining the size of the neighborhood is often one of the critical parameters in the pipeline.
+Local feature descriptors are often split into two different categories, spatial and geometrical histograms \cite{Salti2014}.
 Global feature descriptors, typical computes a descriptors by considering the spatial and/or geometrical relations between two or more local feature descriptors on a 3D geometry.
-
-Local shape features can be split into two different categories, spatial and geometrical histograms \cite{Guo2015}. 
-Early work by Stein and Medioni \cite{Stein1992} used a combination of edges and small surfaces patches for 3D matching in range images.
-Later Johnson  and Albert introduced Spin Images \cite{Johnson1999}
-
-Spin Images \cite{Johnson1999}\\
-Froome \etal \cite{Frome2004} presented a local descriptor 3D shape context.
-%USC \cite{usc2010}\\
-
-%PFH \cite{Rusu2008}
-%FPFH \cite{Fpfh2009}\\
-%ECSAD \cite{Ecsad2015}\\
-%ROPS \cite{Guo2013}\\
-%SHOT \cite{Salti2014}\\
-%NDHIST\\
-%PPF \cite{Drost2010}\\
-%SHOT \cite{Tombari2010}\\
-
-Recently, a couple of benchmarks of local feature descriptors has been presented. Guo \etal \cite{Guo2015} presented a comprehensive comparison of most common local feature descriptors. The 
-Feature Fusion \cite{Buch2016}\\
-Feature comparision Yulan et.al. \cite{Guo2015}
+{\color{blue} TS I would remove the last sentence about global descriptors.}
 

### 2016-07-12 paper.tex
1

--- 2016-06-21 paper.tex
@@
 \usepackage{url}
+\usepackage{subfigure}
+\usepackage{graphicx}
+\usepackage{caption}
+\usepackage{array}
+%\usepackage{arydshln}
 
@@
 \begin{abstract}
-  This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-This is dummy text.
-To be written...........
+This paper presents a new large scale dataset suited for evaluation of local shape descriptors and 3d object recognition algorithms.
+The dataset consists of 3200 scenes and 45 different 3D object models.
+The individual scenes contain 10 occluded objects where the objects belongs to different geometric groups; concave, convex, cylindrical and flat 3D object models.
+The object models have varying amount of local geometric features to challenge existing local shape feature descriptors in terms of descriptiveness and robustness.
+The dataset is validated in a benchmark which evaluates the matching performance of 7 different state-of-the-art local shape descriptors.
+Further, we validate the dataset in a 3D object recognition pipeline.
+Our benchmark shows as expected that local shape feature descriptors without any global point relation across the surface have a poor matching performance with flat and cylindrical objects.
+It is our objective that this dataset contributes to the future development of next generation of 3D object recognition algorithms.
+The dataset will be made public available.
 \end{abstract}
@@
 \section{Introduction} %Hvad, hvorfor, hvordan
-The ability to recognise objects in range images is a fundamental research area in computer vision with many different application areas.
-With continually introduction of new affordable 3D sensors for different applications, the ability to localize and recognize rigid and no rigid objects are a attractive and unavoidable technology in the future.
-Applications areas such as robotic assembly, bin-picking, mobile manipulation, biometric analysis, tracking and intelligent surveillance all benefits from 3D data for recognizing and localizing objects.
-Mainly, because the third dimension are explicit given and not inferred as known from 2D object pose estimation.
-In the last decades a huge effort in 2D object recognition and classification has been going on, where methods have been evaluated on large-scale dataset like the PASCAL Visual Object Challenge (VOC) \cite{Everingham2014} and ImageNet \cite{Imagenet2009}.
-The ability to evaluate algorithms with a large-scale dataset has proven valuable in the future algorithm development after the release of the PASCAL VOC and ImageNet datasets \cite{Everingham2014}.
+Object recognition in range images is a fundamental research area in computer vision with many different applications in different industries.
+With the continually introduction of new inexpensive 3D sensors for different applications, the ability to localize and recognize rigid and no rigid objects is an attractive and unavoidable technology in the future.
+Applications areas such as robotic assembly, bin-picking, mobile robotic manipulation, biometric analysis, tracking and intelligent surveillance all benefits from 3D data for localizing objects.
+Mainly, because the third dimension is explicit given and not inferred as in 2D object pose estimation.
+In the last decades many contributions on 2D object recognition and classification have been published, where methods are evaluated on large-scale dataset like the PASCAL Visual Object Challenge (VOC) \cite{Everingham2014} and ImageNet \cite{Imagenet2009}.
+The benefit from evaluating algorithms on a large-scale dataset has proven valuable in the continues improvement of recognition algorithms after the release of the PASCAL VOC and ImageNet datasets \cite{Everingham2014}.
 \begin{figure}[t]
 \centering
-\includegraphics[width=0.8\linewidth, height= 0.8\linewidth, keepaspectratio]{img/scenes/scene_000.pdf}
-\caption{Example of a scene}
+\includegraphics[clip, trim=14cm 5cm 10cm 5cm,width=0.8\linewidth, height= 0.8\linewidth, keepaspectratio]{img/scenes/full_scene00.png}
+\caption{Example of a full registered scene included in the dataset}
 \label{fig:scene}
 \end{figure}
-In 3D object recognition and pose estimation there still is a need for a large-scale dataset that consistes of 3D querie models $Q_n$, 3D target scenes $S_t$ and ground truth poses $T_{gt}$ for each object in each scene, in order to be able to evaluate 3D object recognition algorithms better.
-Until today 3D object recognition has been evaluated at up to eight smaller datasets \cite{Guo2015}, include in the UWA \cite{Mian2006},\cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2007} and Bologna \cite{Salti2014},\cite{Tombari2010} dataset.
-Other, smaller dataset like the Vienna Kinect\cite{Aldoma2012}, TUM \cite{Rodola2013}, TUM-LineMod\cite{Hinterstoisser2012}, BigBird\cite{BigBIRD} and RGB-D dataset version 1 \& 2\cite{Lai2011}, \cite{Lai2014} have been proposed.
-Common for all dataset are that the amount of scenes and/or models are limited.\\
+In 3D object recognition research, large-scale datasets that consist of a set of 3D querie models $Q_n$, 3D target scenes $S_t$ and ground truth poses $T_{gt}$ for each object in each scene are required in order to be able to evaluate existing and future 3D object recognition algorithms better.
+Until now, 3D object recognition algorithms are evaluated with eight smaller datasets \cite{Guo2015}, including in the UWA \cite{Mian2006},\cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2007} and Bologna \cite{Salti2014},\cite{Tombari2010} datasets.
+Other, smaller dataset like the Vienna Kinect\cite{Aldoma2012}, TUM \cite{Rodola2013}, TUM-LineMod\cite{Hinterstoisser2012}, BigBird\cite{BigBIRD} and RGB-D dataset version 1 \& 2\cite{Lai2011}, \cite{Lai2014} are proposed.
+Common for all datasets is that the amount of scenes and/or models are limited.\\
+
+In this paper we present a new large-scale dataset consisting of 45 objects and 3200 scenes.
+The new dataset is recorded systematically in an environment without ambient light and with controlled illumination.
+The system includes an industrial robot in a dark chamber, a high precision structured light scanner which records data of 292 different scenes from 11 different view points.
+Each scene consists of 10 occluded objects, automatic taken with the structured light sensor, which results in a dataset with around 32000 unique object poses.
+With 11 different views of the same scene our dataset is especially suited for studying the effect of view point changes in 3D object recognition.
+The objects are configured as a classic table-top scenario where different objects are depicted for the side.
+The dataset is not meant as an evaluation platform for bin-picking and top-view scenarios where many instances of the same object are present in the scene.
+The table-top scenario is selected because it encapsulate many of the problems and challenges in 3D object recognition in favour of a larger research community.
+Our 45 object models are scanned in a similar dark chamber with a high precision structured light scanner and a rotation table.
+With this setup we are able to scan objects with an average point resolution of 275 microns.
+We validate our dataset by evaluating state of the art local shape features in a 3D object recognition pipeline.\\ %In Table \ref{tab:datasets} a summery of the features of ours and state of the art dataset are presented.\\
+\textit{Why does the 3D Object recognition community need another dataset?} Previous proposed datasets are limited in the total number of objects, object per.
+scene and total number of scenes.
+Additional, the included objects in the different datasets are mostly geometrical ideal objects.
+With geometrical ideal objects we refers to objects with concave water tight and closed surfaces that are rich of natural local descriptive geometrical features, like the UWA-chef model \cite{Mian2006},\cite{Mian2010}, the bologna-Armadillo \cite{Salti2014},\cite{Tombari2010} and the Queens-BigBird \cite{Taati2007},\cite{Taati2007}.
+In our dataset we include not only ideal concave objects, but flat, cylindrical, feature-rich, simple concave and convex objects.
+It is expected that some local shape features will have a poor performance on our dataset because the lack of local geometric features.
+However, our main goal for proposing this dataset is to strengthen the focus on the challenges in 3D object recognition research and future algorithm development.
+This work is initiated because of previous experiences on pose estimation of geometric simple objects in an industrial robotic context.
+We hope that new novel methods for 3D object recognition will emerge in the future as a side-effect of this dataset.
+Not only local shape descriptos but to a great extend features that uses point relations across the surface e.g.
+Point Pair Features \cite{BirdalIlic2015}, semi-global features and template matching.
+
+Our objects are a combination of lab-objects and industrial objects, selected from companies that want to pick these objects from boxes or bins with a robot.\\
+This paper is structured as follows: In Section \ref{sec:related_work} related datasets and local feature descriptors are presented.
+Section \ref{sec:exp_design} outlines our experimental design followed by Section \ref{sec:benchmark} which presents our benchmarking methodology.
+In Section \ref{sec:evaluation} the results are given followed by a discussion and conclusion in Section \ref{sec:conclusion}.
 %\begin{multicols}{3}
@@
 \centering % Center table
-         \begin{tabular}{p{4.2cm} p{0.3cm} p{1.2cm} p{1.5cm} p{1.55cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm}}
+         \begin{tabular}{p{4.5cm} p{0.3cm} p{1.2cm} p{1.5cm} p{1.55cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm}}
                   %%  & \multicolumn{2}{c}{Data Size} & \multicolumn{4}{c}{Models} & \multicolumn{2}{c}{Scene} & \multicolumn{5}{c}{Ground truth} & he \\
                   %%  \hline
-             & {$M_q$} & {$S_t$} &  Sensor & {$M_q$} in {$S_t$} & \rotatebox{90}{$M_q$ normals} & \rotatebox{90}{$M_q$ color } & \rotatebox{90}{$M_q$ mesh } & \rotatebox{90}{$S_t$ normals } & \rotatebox{90}{$S_t$ color } & \rotatebox{90}{$S_t$ mesh} & \rotatebox{90}{Full 6D pose} & \rotatebox{90}{Occlusion} & \rotatebox{90}{Clutter} & \rotatebox{90}{[R]/[S]}\\
+             & {$M_q$} & {$S_t$} &  Sensor & {$M_q$} in {$S_t$} & \rotatebox{90}{$M_q$ normals} & \rotatebox{90}{$M_q$ mesh } & \rotatebox{90}{$S_t$ normals } & \rotatebox{90}{$S_t$ mesh} & \rotatebox{90}{Full 6D pose} & \rotatebox{90}{Occlusion} & \rotatebox{90}{Clutter} & \rotatebox{90}{[R]/[S]}\\
             \hline
             \hline
-             UWA \cite{Mian2006}, \cite{Mian2010}  & 5 & 50 & LIDAR & (5)/(5) & \checkmark & \% & \checkmark & \checkmark & \%  & \checkmark & \checkmark  & \checkmark & \% & R\\
+             UWA \cite{Mian2006}, \cite{Mian2010}  & 5 & 50 & LIDAR & (5)/(5) & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark  & \checkmark & \% & R\\
              \hline
-             Queens Lidar  \cite{Taati2011}, \cite{Taati2007}  & 5 & 80 & LIDAR & (1-5)/(1-5) & \checkmark & \% & \checkmark & \% & \%  & 0 & \checkmark & \% & \% & R\\
+             Queens Lidar  \cite{Taati2011}, \cite{Taati2007}  & 5 & 80 & LIDAR & (1-5)/(1-5) & \checkmark  & \checkmark & \%  & 0 & \checkmark & \% & \% & R\\
              \hline
-             Queens Stereo  \cite{Taati2011}, \cite{Taati2007}  & 5 & 100 & Stereo & (3)/(3)   & \checkmark & \% & \checkmark & \% & \%  & 0 & \checkmark & \% & \% & R\\
+             Queens Stereo  \cite{Taati2011}, \cite{Taati2007}  & 5 & 100 & Stereo & (3)/(3)   & \checkmark & \checkmark & \%  & 0 & \checkmark & \% & \% & R\\
              \hline
-             Bologna 1\&2 \cite{Salti2014}, \cite{Tombari2010} & 6 & 45 & LIDAR & (3-5)/(3-5) & \checkmark & \% & \checkmark & \checkmark & \% & \checkmark & \checkmark & \% & \% & S \\
+             Bologna 1\&2 \cite{Salti2014}, \cite{Tombari2010} & 6 & 45 & - & (3-5)/(3-5) & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \% & \% & S \\
 			 \hline              
-             Bologna 3 \cite{Salti2014}, \cite{Tombari2010} & 8 & 15 & Spacetime & (2)/(5-6) & \checkmark & \checkmark & \% & \checkmark & \checkmark & \checkmark & \checkmark & \% & \% & R\\
+             Bologna 3 \cite{Salti2014}, \cite{Tombari2010} & 8 & 15 & Spacetime & (2)/(5-6) & \checkmark & \% & \checkmark & \checkmark & \checkmark & \% & \% & R\\
              \hline
-             Bologna 4 \cite{Salti2014}, \cite{Tombari2010} & 8 & 16 & Spacetime & (2)/(6) & \checkmark & \checkmark & \% & \checkmark & \checkmark & \checkmark & \checkmark & \% & \% & R\\
+             Bologna 4 \cite{Salti2014}, \cite{Tombari2010} & 8 & 16 & Spacetime & (2)/(6) & \checkmark & \% & \checkmark & \checkmark & \checkmark & \% & \% & R\\
              \hline
-             Bologna 5 \cite{Salti2014}, \cite{Tombari2010} & 6 & 16 & Kinect V1 & (2-4)/(5-9) & \checkmark & \checkmark & \% & \checkmark & \checkmark & \checkmark & \checkmark & \% & \% & R \\
+             Bologna 5 \cite{Salti2014}, \cite{Tombari2010} & 6 & 16 & Kinect V1 & (2-4)/(5-9) & \checkmark & \% & \checkmark & \checkmark & \checkmark & \% & \% & R \\
              \hline
-             Vienna Kinect \cite{Aldoma2012} & 35 & 50 & Kinect V1 & 0 & \checkmark & \% & \checkmark & \% & \checkmark & 0 & \checkmark & \% & \% & R\\
+             Vienna Kinect \cite{Aldoma2012} & 35 & 50 & Kinect V1 & 0 & \checkmark & \checkmark & \% & 0 & \checkmark & \% & \% & R\\
              \hline
-             RGB-D Scenes V1 \cite{Lai2011}, \cite{Lai2012} & 5 & 8 videos & Kinect V1 & (0)/ & \% & \% & \%  & \% & \checkmark  & \% & \% & \% & \% & R\\
+             RGB-D Scenes V1 \cite{Lai2011}, \cite{Lai2012} & 5 & 8 videos & Kinect V1 & (0)/ & \% & \%  & \%  & \% & \% & \% & \% & R\\
 			 \hline             
-             RGB-D Scenes V2 \cite{Lai2014} & 9 & 14 & Kinect V1 & (0)/ & \% & \% & \% & \% & \checkmark & \% & \% & \% & \% & R\\
+             RGB-D Scenes V2 \cite{Lai2014} & 9 & 14 & Kinect V1 & (0)/ & \% & \% & \% & \% & \% & \% & \% & R\\
              \hline
-             T{\"U}M \cite{Rodola2013} & 20 & 150 & kinect & (3-5)/(3-5) & \checkmark  & \%  & \checkmark  & \checkmark & \% & \checkmark & \checkmark & \checkmark & \checkmark & S\\
+             T{\"U}M \cite{Rodola2013} & 20 & 150 & - & (3-5)/(3-5) & \checkmark  & \checkmark  & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & S\\
              \hline
-             Willow \cite{Willow} & 35 & 177 & kinect & 0 & \checkmark  & \checkmark  & \checkmark  & \% & \checkmark & 0 & \% & \% & \% & R\\
+             Willow \cite{Willow} & 35 & 177 & Kinect V1 & 0 & \checkmark  & \checkmark  & \% & 0 & \% & \% & \% & R\\
              \hline
@@
             % \hline
-             ECCV12 \cite{Aldoma2012}  & 35 & 50 & Kinect V1 & (3-7)/(3-7) & \%  & \checkmark  & \checkmark  & \% & \% & \% & \checkmark & \% & \% & R\\
+             ECCV12 \cite{Aldoma2012}  & 35 & 50 & Kinect V1 & (3-7)/(3-7) & \% & \checkmark  & \% & \% & \checkmark & \% & \% & R\\
              \hline
-              Alicante \cite{Garcia-Garcia2016}  & 30 & 50 & Kinect V2 & (0)/(0) & \%  & \checkmark  & \checkmark  & \% & \% & 0 & \checkmark & \% & \% & R\\
+              Alicante \cite{Garcia-Garcia2016}  & 30 & 50 & Kinect V2 & (0)/(0) & \% & \checkmark  & \% & 0 & \checkmark & \% & \% & R\\
              \hline
              \hline
-             \textbf{Our SL dataset}  & \textbf{50} & \textbf{3300} & SL & (10)/(10) & \checkmark  & \checkmark  & \checkmark  & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark & R\\
-             \hline
-             \textbf{Our Kinect dataset}  & \textbf{50} & \textbf{3300} & Kinect V2 & (10)/(10) & \checkmark  & \checkmark  & \checkmark  & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark & R\\
+             \textbf{Our dataset}  & \textbf{45} & \textbf{3200} & SL & (10)/(10) & \checkmark  & \checkmark  & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark & R\\
+          %   \hline
+         %    \textbf{Our Kinect dataset}  & \textbf{50} & \textbf{3300} & Kinect V2 & (10)/(10) & \checkmark  & \checkmark  & \checkmark  & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark & R\\
              \hline 
@@
 %        \captionof{table}{Existing datasets for 3D object recognition and pose estimation}% Add 'table' caption
-        \label{dataset_overview}
+        \label{tab:dataset_overview}
 
@@
 %\end{multicols}
-In this work we present a new large-scale dataset consisting of 50 objects and 3300 scenes.
-The new dataset is recorded systematically in an environment without ambient light and with controlled illumination.
-The system includes a industrial robot in a dark chamber, a high precision structured light scanner and a Kinect V2 sensor, which records data from 11 different view points.
-Each scene consists of 10 objects automatic taken with the two different sensors, which results in a dataset with around 66000 unique object poses.
-With 11 different views of the same scene our dataset is especially suited for studying the effect of view point changes in 3D object recognition.
-Our 50 object models are scanned in a similar dark chamber with a high precision structured scanner and a rotation table.
-With this setup we are able to scan objects with an accuracy down to XX microns.
-We use the dataset to evaluate state of the art local shape features in a 3D object recognition pipeline.
-In Table \ref{tab:datasets} a summery of the features of ours and state of the art dataset are presented.\\
-Why do the 3D Object recognition community needs another dataset?
-Current proposed dataset is limited in the number of objects/scenes and the objects included in the datasets are mostly geometrical ideal objects.
-With geometrical ideal objects we refers to mostly concave objects that are rich of geometrical features like the UWA-chef model \cite{Mian2006},\cite{Mian2010}, the bologna-Armadillo \cite{Salti2014},\cite{Tombari2010} and the Queens-BigBird \cite{Taati2007},\cite{Taati2007}.
-With our dataset we introduce not only ideal concave objects, but flat, cylindrical, feature-rich and feature-poor concave and convex objects.
-Our objects are a combination of lab-objects and industrial objects which are selected from companies that wants to pick these objects from boxes or bins with a robot.\\
-This paper is structured as follows: In Section \ref{sec:related_work} related datasets and local feature descriptors are presented.
-Section \ref{sec:exp_design} details our experimental design followed by Section \ref{sec:benchmark} which presents our benchmarking methodology.
-In Section \ref{sec:evaluation} the results are given followed by a discussion and conclusion in Section \ref{sec:conclusion}.
 %-------------------------------------------------------------------------
-	\section{Related work} \label{sec:related_work}
+\section{Related work}\label{sec:related_work}
 %We are not considering learning approaches
+\noindent
 \textbf{3D Object Recognition datasets:}\\
+The last 10 years a few 3D object recognition datasets have been published.
+Mainly in conjunction with algorithms for local feature description \cite{Mian2006},\cite{Taati2007},\cite{Taati2011},\cite{Tombari2010},\cite{Salti2014}, correspondence matching and rejection \cite{Rodola2013}, pose hypothesis verification \cite{Aldoma2012} and 3D keypoint detection \cite{Mian2010}.
+Common for all existing dataset are the limited number of 3D object models and scenes.
+A comparison of the different datasets are presented in Table \ref{tab:dataset_overview}.
+The most common used datasets are the UWA  \cite{Mian2006}, \cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2011} and the Bologna \cite{Salti2014}, \cite{Tombari2010}.
+These datasets are widely used in performance evaluations of  local feature descriptors \cite{Guo2015}, \cite{Buch2016}, keypoint detectors \cite{Salti2011} and surveys \cite{Guo2014}, \cite{FilipeAlexandre2014}.
+The main problems of all the datasets are; size, variety of objects and occlusion/clutter estimates.
+The recent comparison studies \cite{Buch2016},\cite{Guo2015} revival that the data for evaluation is not good enough to scientific distinguish results.
+The studies showed that the performance of one local feature descriptor is poor when evaluated on one dataset but fail in other datasets.
+These results reveal that a larger data foundation is required in the quest to find shape features which generalize over many object categories.\\
 
+\noindent
 \textbf{Local feature descriptors:}\\
-During the last three decade, a vast number of different 3D local feature descriptors have been proposed including SPLASH \cite{Stein1992}, Spin Image (SI) \cite{Johnson1999}, 3DSC \cite{Frome2004}, LSP \cite{ChenBhanu2004}, 3D Tensor \cite{Mian2006}, THRIFT \cite{Flint2007}, MESH-HOG \cite{Zaharescu2009}, ISS \cite{Zhong2009}, USC \cite{usc2010}, PFH \cite{Rusu2008}, FPFH \cite{Fpfh2009}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015}, Tri-Spin-Image (TriSI)\cite{Guo2015}.
-The descriptors find usages in applications such as 3D object categorization, recognition, retrial, analysis, registration and reconstruction among others.
-Designing descriptors which are distinctive and robust to occlusion and noise are still and ongoing research topic.
-Recent studies has shown that the proposed features are not generalizing well over many types of geometry classes, \cite{Guo2015},\cite{Buch2016}.
-The studies proved one of the main issue in 3D object recognition today, namely the fact that there exist no local shape feature that describes the geometry well in many different object classes, e.g.
-flat, rotational symmetrical and geometrical feature rich objects.
-What feature(s) to use are still dependant of the object geometry.
-These studies poses a relevant research question, are the local feature descriptors not descriptiveness enough to generalize over different object classes or are the evaluation data to limited?
-The evaluation dataset there are used for the evaluation in general and in \cite{Guo2015},\cite{Buch2016}, consists mainly of objects with many descriptive and distinctive geometrical features.
-In this work we try to answer this fundamental question by creating the data foundation to evaluate the performance of each local feature descriptors by applying statistic.
-
-Local feature descriptor aims at computing a distinctive and robust N-dimensional feature vector around a point, by considering the k-neighbour points in euclidean space.
-The radius of the K-Nearest Neighbour search (KNN), the support radius is often one of the critical parameters in the pipeline.
-Local feature descriptors are often split into tow different categories, spatial and geometrical histograms \cite{Guo2015}.
-Global feature descriptors, typical computes a descriptors by considering the spatial and/or geometrical relations between two or more local feature descriptors on a 3D geometry.
-
-Local shape features can be split into two different categories, spatial and geometrical histograms \cite{Guo2015}. 
-Early work by Stein and Medioni \cite{Stein1992} used a combination of edges and small surfaces patches for 3D matching in range images.
-Later Johnson  and Albert introduced Spin Images \cite{Johnson1999}
-
-Spin Images \cite{Johnson1999}\\
-Froome \etal \cite{Frome2004} presented a local descriptor 3D shape context.
-%USC \cite{usc2010}\\
-
-%PFH \cite{Rusu2008}
-%FPFH \cite{Fpfh2009}\\
-%ECSAD \cite{Ecsad2015}\\
-%ROPS \cite{Guo2013}\\
-%SHOT \cite{Salti2014}\\
-%NDHIST\\
-%PPF \cite{Drost2010}\\
-%SHOT \cite{Tombari2010}\\
-
-Recently, a couple of benchmarks of local feature descriptors has been presented. Guo \etal \cite{Guo2015} presented a comprehensive comparison of most common local feature descriptors. The 
-Feature Fusion \cite{Buch2016}\\
-Feature comparision Yulan et.al. \cite{Guo2015}
+During the last three decades, a vast number of different 3D local feature descriptors have been proposed including SPLASH \cite{Stein1992}, Spin Image (SI) \cite{Johnson1999}, 3D Shape Context (3DSC) \cite{Frome2004}, LSP \cite{ChenBhanu2004}, 3D Tensors \cite{Mian2006}, THRIFT \cite{Flint2007}, MESH-HOG \cite{Zaharescu2009}, ISS \cite{Zhong2009}, Unique shape context (USC) \cite{usc2010}, Point Feature Histogram (PFH) \cite{Rusu2008}, Fast Point Feature Histograms (FPFH) \cite{Fpfh2009}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015} and Tri-Spin-Image (TriSI)\cite{Guo2015}.
+The descriptors find usages in applications such as 3D object categorization, recognition, retrieval, analysis, registration and reconstruction among others.
+Designing descriptors which are distinctive and robust to occlusion and noise is still an ongoing research topic.
+Recent studies have shown that the proposed features are not generalizing well over many types of geometry classes, \cite{Guo2015},\cite{Buch2016}.
+The studies proved one of the main issues in 3D object recognition today, namely the fact that there exist no local shape feature that describes the geometry well over many different object classes, e.g.
+flat, rotational symmetrical and geometrically feature rich objects.
+What feature(s) to use are still dependent on the object geometry.
+These studies pose a relevant research question; are the local feature descriptors not descriptive enough to generalize over different object classes or are the data used for evaluation too limited?
+The evaluation datasets used for the evaluation in general and in \cite{Guo2015},\cite{Buch2016} consist mainly of objects with many descriptive and distinctive geometrical features.\\
+Local feature descriptors aim at computing a distinctive and robust N-dimensional feature vector around a point, by considering the points in an Euclidean neighbourhood.
+The support radius determining the size of the neighbourhood is often one of the critical parameters in the pipeline.
+Local feature descriptors are often split into two different categories, spatial and geometrical histograms \cite{Salti2014}.
+%Global feature descriptors, typical computes a descriptors by considering the spatial and/or geometrical relations between two or more local feature descriptors on a 3D geometry.
+{\color{blue} TS I would remove the last sentence about global descriptors.}
 
@@
 %Limitations in current dataset and algorithms. Feature rich objects not flat or cylindrical objects
-
-%The UWA dataset by Mian et.al.
-\cite{Mian2006}, \cite{Mian2010} is one of the best known datasets for 3D pose estimation algorithm evaluation.
-The dataset is composed of four full object models and 50 real scenes captures with a laser scanner which containing incomplete instances of the objects.
-Each scene contains three or four object models which results in much clutter and occlusion.
-The amount of occlusion and clutter in each scene is not provided.
-The four object models are generated with a multi-view registration algorithm.
-Each object model contain more than 100000 mesh vertices and posses good and distinctive shape features with non-uniform surfaces and ambiguities.
-The object models and scenes has pre-estimated normals and no color/texture.
-The dataset contains full 6D ground truth poses for each object as the only evaluation data type.
-
-%The Queens Lidar dataset \cite{Taati2011}, \cite{Taati2007} is constructed like the UWA dataset with a laser scanner and consists of five object models and 80 real scenes take from one viewpoint.
-Like the UWA dataset, the Queens Lidar dataset contains no color information but the scenes has larger variation compared to the UWA dataset with one to five object models present in the scenes.
-The five object models has pre-estimated normals but is only provided as a point representation.
-The dataset contains full 6D ground truth poses for each object as the only evaluation data.
-
-%The Queens Stereo dataset \cite{Taati2011}, \cite{Taati2007} contains five full object models and 100 real scenes created with a stereo camera and standard stereo reconstruction.
-The dataset is taken from one viewpoint.
-Each scene contains three object models with no color, normal, occlusion or clutter information available.
-Like the Queens Lidar dataset the object models is represented with points and no vertices.
-The dataset contains full 6D ground truth poses for each object as the only evaluation data.
-
-%The Bologna 1 \& 2 dataset \cite{Salti2014}, \cite{Tombari2010} contains six full object models and 45 synthetic scenes.
-All scenes is construct a synthetic scenes with models from the Stanford 3D Scanning Repository.
-Each 45 scenes are created by applying a random transformation to a random subset of object model and store the scene.
-The difference between the Bologna 1 and Bologna 2 dataset are that Bologna 2 is re-sampled 1/8 of the original point density.
-The fact that it is a synthetic dataset results in 100 percent accurate 6D ground truth data.
-%The Bologna 3 dataset \cite{Salti2014}, \cite{Tombari2010} contains eight models and 15 scenes.
-Each scenes are acquired with spacetime stereo technique and contains both color and surface normal information.
-Each scene contains two object models and additional objects to create clutter and occlusion.
-The eight models are single view object templates with color and estimated normals in mesh representation.
-The dataset contains full 6D pose estimates as ground truth.
-Their exist no data on occlusion and clutter estimates.
-%The Bologna 4 dataset \cite{Salti2014}, \cite{Tombari2010} contains eight models and 16 scenes.
-As Bologna 3, this dataset is acquired with spacetime stereo techniques and containing color and normal data for both the object models and the scenes.
-The dataset includes object models with highly similar shapes but different textures.
-Each scene contains two object models and additional objects to create clutter and occlusion.
-The eight models are single view object templates with color and estimated normals in mesh representation.
-The dataset contains full 6D pose estimates as ground truth.
-Their exist no data on occlusion and clutter estimates.
-%The Bologna 5 dataset \cite{Salti2014}, \cite{Tombari2010} contains six object models and 16 scenes.
-The dataset is acquired with a Microsoft Kinect sensor and includes color and normal information for both the object models and scenes.
-The provided object models is a set of object templates taken from different views.
-With a proper mesh registration algorithm a full object model can be created.
-The dataset contains full 6D pose estimates as ground truth.
-Their exist no data on occlusion and clutter estimates.
-%The Vienna Kinect dataset \cite{Aldoma2012} contains 35 full object models and 50 scenes.
-Each scene is acquired with a Microsoft Kinect sensor and includes color information but no pre-estimated normals.
-All scenes is table top scenes with limited occlusion and clutter.
-The object models in each scene is distThe 35 object models are full represented mesh models without color but includes pre-estimated normals.
-%The dataset contains full 6D pose estimates as ground truth. Their exist no data on occlusion and clutter estimates.
-%TUM dataset \cite{Rodola2013}\\
-%RGB-D Dataset V1 \cite{Lai2011}, \cite{Lai2012}\\ 
-%RGB-D Dataset V2 \cite{Lai2014}\\ 
 %------------------------------------------------------------------------
@@
 In addition, a high precision turntable (Newmark Systems RT-5) is used in order to provide automatic rotation of the object.
-Each of the 50 objects are incremental scanned with a rotation of 20 degrees.
+Each of the 45 objects are incremental scanned with a rotation of 20 degrees.
 All individual scan views are reconstructed by the Line shifting algorithm \cite{Guehring2000} which results in accurate and dense point cloud of the objects.
 Eleven temporal binary gray code patterns are projected followed by eight line shifting patterns.
-The point resolution of the scanner is XX.
-Once a single view of the model are scanned, noisy outliers of the measurement are manual removed and surface normals are estimated to ensure consistent normals.
-All 18 views are registered with Iterative Closest Point (ICP) and the object frame are computed by principal component analysis.
-All models are sampled with a Poisson disk sampling algorithm and triangulated with the poisson reconstruction algorithm \cite{Kazhdan2006} with an octree depth=14, Solver divide = x and xx = xx.
+The point resolution of the scanned objects are in average 275 microns and consist of around 908000 vertices and 1.8 million faces in average.
+Once a single view of the model is scanned, noisy outliers of the measurement are manual removed and surface normals are estimated to ensure consistent normals.
+All 18 views are registered with Iterative Closest Point (ICP) and a new object frame is computed with principal component analysis on the point set.
+All models are sampled with a Poisson disk sampling algorithm \cite{Corsini2012} and triangulated with the poisson reconstruction algorithm \cite{Kazhdan2006} with an octree depth=14, solver divide = 8 and iso divide = 5.
 We use the PCL implementation \cite{RusuCousins2011}.
@@
 \subsection{Scene scanning} 
-For the data collection we use the robot depicted at Figure \ref{fig:robot}.
-The robot is equipped with two PointGray Grasshopper3 GS3-U391S6C-C USB3 color cameras with resolution of 9.1 Mp, a Wintech Pro4500 projector with a resolution of 1140x912 pixels and a Kinect One sensor.
-The sensor cluster is mounted in the robot tool.
-The sensor modalities are selected by two reasons.
+For the data collection we use a 6-axis ABB IRB 1600 industrial robot to provide a precise and highly repeatable camera pose.
+The robot is depicted in Figure \ref{fig:robot}.
+The robot is equipped with two PointGray Grasshopper3 GS3-U391S6C-C USB3 color cameras with resolution of 9.1 Mp and a Wintech Pro4500 projector with a resolution of 1140x912 pixels.
+The sensor cluster with the structured light sensor (SL) is mounted in the robot tool.
+%The sensor modalities are selected by two reasons.
 First, the structured light system (SL) ensure a high precision that is XX times better than the Kinect thus we are able to provide accurate ground truth pose data for each object in the scene down to a precision of xx mm.
 Second, Time-of-Flight sensors like the Kinect One sensor are popular sensors in many research areas such as robotic manipulation, 3D semantic mapping, people detection and consumer products thus we wanted to support the future development of 3D object recognition systems and algorithms by including the sensor in the dataset.
+\begin{figure}[ht]
+\centering
+\includegraphics[width=1.0\linewidth, height= 0.7\linewidth]{Robot.pdf}
+\caption{Scan of the full scene with view frames}
+\label{fig:robot}
+\end{figure}
 The Robot setup is constructed as a radiometric "dead" which gives a scene representation with zero ambient light.
-All the scene illumination is controlled in the recording process.
-The sensor cluster is calibrated with a automatic calibration procedure which includes a stereo calibration of the SL sensor using \verb|OpenCV|\footnote{\url{http://opencv.org/}} and a intrinsic calibration of the Kinect using the \verb|iai_kinect2|\footnote{\url{https://github.com/code-iai/iai_kinect2}} software package.
+All scene illumination is controlled in the recording process.
+The sensor cluster is calibrated with an automatic calibration procedure which includes a stereo calibration of the SL sensor using \verb|OpenCV|\footnote{\url{http://opencv.org/}}.% and a intrinsic calibration of the Kinect using the \verb|iai_kinect2|\footnote{\url{https://github.com/code-iai/iai_kinect2}} software package.
 The Kinect calibration ensure a proper registration of the RGB values at each 3D point.
-An automatic hand eye calibration \cite{DornaikaHoraud1998} is conducted in order to align the Kinect and the SL scans in the world frame.
-The world frame is the robot base frame.
-%Describe recording procedure
-Each scene are scanned from 11 different views with both the structured line scanner (SL) and the Kinect such that each physical scene results in 11 SL and 11 Kinect scenes, 22 scenes in total.
-During the SL scanning process the chamber is completlty dark in order to increase the signal-to-noise ration of the scan.
-When the Kinect scene are depicted a two diffuse light projectors are automatical turned on to depict the kinect colors.
-The level of diffuse scene ligth are empirical dertermined such that the kinect RGB camera not oversaturating.
+An automatic hand eye calibration \cite{DornaikaHoraud1998} is conducted in order to align the structured light scans in the world frame.
+The world frame is placed in the robot base frame.
+Each physical scene is scanned from 11 different views with the structured line scanner (SL).
+During the structured light scanning process the chamber is completely dark in order to increase the signal-to-noise ration of the scan.
 The structured light scans are reconstructed with the Line shifting algorithm \cite{Guehring2000} with ten temporal pattern levels.
 The views are distributed equally on a quarter sphere around the scene, such that each scene is depicted from - 90 to 90 degrees horizontally and 0 to 45 degree vertically.
-In order to reproduce the results we store raw Portable Network Graphics images in full resolution (9.1 MP).
+The distance between the sensor views and the center of the scene is 0.8 meter.
+In order to be able to reproduce the results we store all images in raw Portable Network Graphics in full resolution (9.1 MP).
 De-bayering, white balance, image rectification, pattern decoding and point cloud reconstruction are a off line process.
-
+\begin{figure}[ht]
+\centering
+\includegraphics[clip, trim=12cm 6cm 12cm 8cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/mesh_scene.png}
+\caption{Example on one of the 3200 triangulated scene}
+\label{fig:mesh_scene}
+\end{figure}
 %Meshing of the scenes + normal estimation
-%\begin{figure}[ht]
-%\centering
-%\includegraphics[width=1.0\linewidth, height= 0.7\linewidth]{img/dummy.pdf}
-%\caption{Scan of the full scene with view frames}
-%\label{fig:scene}
-%\end{figure}
+Local shape features like 3D Tensor \cite{Mian2006}, ROPS \cite{Guo2013} and FPFH \cite{Fpfh2009} apply the underlying mesh surface during feature computation.
+In order for the dataset to support these algorithms all scenes are triangulated to a polygonal mesh.
+For each scene a set of corresponding triangles are computed with a 2D delaynay triangulation algorithm in VTK\footnote{\url{http://www.vtk.org/}}.
+Each $(x,y)$ point coordinates of the scene point cloud are normalized with its $z$ component in order to project the 3D point cloud into 2D and triangulated.
+The 3D mesh structures are created by re-assigning all 3D point with the triangles of the same index.
+Long edges in the mesh are then removed form the mesh in order to avoid triangles between step edges.
+An example of a triangulated scene is shown in Figure \ref{fig:mesh_scene}.
 %A Note on ground truth
 \subsection{Ground Truth 6D pose}
-For each of the ~3300 scenes the 6D ground truth pose, occlusion and clutter estimates for each object are provided.
-We estimate the occlusion from Equation \ref{eq:occlusion} and clutter from Equation \ref{eq:clutter} by counting the number of points at the object model which squared euclidean distance to a scene point is less than two times the resolution.
+For each of the 3200 scenes the 6D ground truth pose, occlusion and clutter estimates for each object are provided.
+We estimate the occlusion from Equation \ref{eq:occlusion} and clutter from Equation \ref{eq:clutter} by counting the number of points at the object model in which the squared euclidean distance to a scene point is less than two times the scene resolution.
 Both the object model and the scene are sampled to ensure equal point distance.
 \begin{equation}
-Occlusion = 1 - \frac{visible object points}{total object points} 
+Occlusion = 1 - \frac{visible \: object \: points }{total \: object \: points} 
 \label{eq:occlusion}
@@
 \begin{equation}
-Clutter = 1 - \frac{visible object points}{total scene points}
+Clutter = 1 - \frac{visible \: object \: points}{total \: scene \: points}
 \label{eq:clutter}
 \end{equation}
-Accurate ground true poses are ensure by registration of the individual SL scans into one full scene model in world frame which covers the geometric structures of all the models in the particular scene, see Figure \ref{fig:scene}.
-The hand/eye calibration procedure computes the transformation from each sensor frame to the robot flange such that every transformation is known in the system.
-With all transformation known, it is trivial to align the kinect scans with full SL scene by applying the transformation $T_{kinect2SL}$ followed by fine ICP registration $T_{ICP}$ on the full resolution SL scene.
-All ~300 combined scenes are manual annotated by selecting four identical points for each model and the scene followed by an estimation of the rigid transform.
-An iterative ICP, which incremental decrease the max allowed correspondence euclidean distance on the full resolution cloud ensures the ground truth pose.
-The individual ground truth poses in each sensor view $T{s_n}$ are generate by transforming ground truth pose from the world frame $T_{w}$ to each of the individual sensor frames $T{s_n}$ by applying the equation $T^{w}_{s_n} = $.
-This methodology guarantees accurate pose in $T{s_n}$ independent of the amount of occlusion.
-Even in views with limited number of scene point of an object the ground truth pose is accurate.
-Moreover, we align each Kinect scans in $T{s_n}$ to the SL scan by applying the transform $T=$ which gives an accurate ground truth pose for the noisy Kinect data based on dense and accurate SL data.
-
-%We provide 6D ground truth poses with RMS error for the final ICP registration. In this way we can guarantee that the overall accuracy of all ground truth poses is within xx mm. 
-%Combine the 11 views. The different scans are then aligned with respect to scan number zero by applying
-%These view points ensure a good coverage of the scene and provide the needed geometric structure of each object to reliable compute ground truth. 
-%alignment two frame 0. alignment of kinect scene and transformation back to the sensor frame.
-
+\indent
+Accurate ground true poses are ensured by manual annotation of each object in the scenes.
+First, one point cloud that covers 180 degree of the scene is stitched together form each of the 11 views and registered with ICP.
+This full scene point cloud is applied in the annotation process, see Figure \ref{fig:scene}.
+The full scene point cloud covers the geometric structures of each model in the scene with more point compared to the individual views.
+Thus, it is possible to get a more accurate ICP registration of the object model in the scenes.
+All 290 combined scenes are manual annotated by selecting four identical points for each model and the scene, followed by an estimation of the rigid transform.
+An iterative ICP, which incremental decreases the allowed correspondence distance ensures a very accurate final ground truth pose of each object in the scene.
+The final ICP iterations are accomplished with the full resolution model to get the best fit of the model points to the scene points.
+The individual ground truth poses in each sensor view $T_{sensor_{n}}$ is computed by transforming the ground truth poses from the world frame $T_{world}$ to each of the individual sensor frames $T_{sensor_{n}}$.
+Equation \ref{eq:transformation} show the final transformation.
+\begin{equation}
+T^{world}_{sensor_{n}} = T^{-1}_{robot} \cdot T^{-1}_{HandEye} \cdot T^{-1}_{icp} \cdot T_{gt}
+\label{eq:transformation}
+\end{equation}
+where $T_{robot}$ is the known robot pose for each view point, $T_{HandEye}$ is the calibrated hand eye transform, $T_{icp}$ is the alignment transform which align view $n$ to view $0$ in the world frame and $T_{gt}$ is the annotated ground truth pose in the full scene point cloud with the world frame as reference.
+This methodology guarantees accurate pose in $T{sensor_{n}}$ independent of the amount of occlusion.
+Even in views with limited number of scene points of an object the ground truth pose is accurate because the ground truth pose is computed in the full scene point cloud.
+For each ground truth pose in each sensor view, we compute the RMS error between the model and the scene to guarantee the overall accuracy of all ground truth poses.
+On average the RMS error of all ground truth poses is within 0.15 mm.
 %-------------------------------------------------------------------------
 \section{Benchmark}\label{sec:benchmark}
-This section describes the experimental protocol defined for the evaluation of the dataset.
-The evaluation is divide into two parts; feature descriptivness and recognition rate.
-The selected local feature descriptors for our evaluation includes; Spin Image (SI) \cite{Johnson1999}, 3DSC \cite{Frome2004}, PFH \cite{Rusu2008}, FPFH \cite{Fpfh2009}, USC \cite{usc2010}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015} and NDHIST \cite{Buch2016}.
-The features are selected based on implementation availability and results from previous studies on feature descriptor benchmarking \cite{Guo2015}, \cite{Buch2016}.
-Precision-Recall Curves (PRC) are used to evaluate the descriptiveness and accuracy of a feature descriptor.
-The
-
-"For each target model, the seed points of each query model are placed in the scene using the ground truth pose, and the target seed points are now described.
-We use voxel gird for sampling \cite{RusuCousins2011} to get uniform point distance.
-Following the seed point sampling, each seed point are described by the nine feature descriptors.
-
-"In general the matching accuracy of a descriptor is expected to increase with increasing support radius, except in cases where occlusion and clutter are present." For fair comparison individually tuned support radii for each descriptors are used; SI($xx$), 3DSC($xx$), PFH($xx$), FPFH($xx$), USC($xx$), SHOT($xx$), ROPS($xx$), ECSAD($xx$), NDHIST($xx$).
-
-For each query and target we add three levels of gaussian noise to the vertex position
+This section outlines the experimental protocol defined to validate the dataset.
+The protocol is inspired by Salti \etal \cite{Salti2014}.
+The evaluation is divide into two parts; feature matching accuracy and object recognition rate.
+The selected local feature descriptors for our evaluation include; Spin Image (SI) \cite{Johnson1999}, PFH \cite{Rusu2008}, FPFH \cite{Fpfh2009}, USC \cite{usc2010}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015} and NDHIST \cite{Buch2016}.
+The features are selected based on implementation availability and results from previous studies on feature descriptor benchmarking \cite{Guo2015},\cite{Buch2016}.
+\subsection{Feature Matching}\label{sec:benchmark_matching}
+The descriptiveness and accuracy of a feature descriptor are measured with Precision-Recall and presented as 1-Precision vs.
+Recall Cruves (PRC).
+First we sample both the query models and the target scenes with a voxel grid sampling \cite{RusuCousins2011} which results in equal point distance.
+The voxel size is tuned to give approximately 1000 seed points per.
+object in both the query and target.
+The target seed points are found by transforming the query seeds into the target by applying the object ground truth pose.
+The target seeds are selected in a nearest neighbour search with a distance threshold.
+A feature descriptor for each seed point in the query and target mesh is computed.
+For fair comparison individually tuned support radii for each descriptors are used.
+We use the following feature resolution multiplier: SI($20$), 3DSC($22.5$), FPFH($17.5$), USC($25$), SHOT($17.5$), ROPS($20$), ECSAD($20$), NDHIST($31$).
+Hence, the radius for each feature is a function of the average model or scene resolution.
+Upon feature computation the underlying scene and object meshes are utilized in 0.25 and 0.05 decimated version; respectively.
+The level of decimation are empirical determined to the level with best overall matching results for all features.
+During decimation the normal orientation is re-computed for each vertex by the area weighted mean of the mesh triangle \cite{Thurmer1998} and normalized.
+In order to resolve the exact number of correct feature matches, a brute-force linear kd-tree search is	 used with a ${L_2}$ distance function.
+Other distance metrics such as ${L_1}$, ${L_\infty}$, are tested in previous work but the best results are achieved with the $L_2$ distance metric.
+Thus, we only present results for the ${L_2}$ metric.
+During matching we are computing the ratio of the nearest and the second-nearest matching distances.
+This matching strategy is adapted from multiple previous studies e.g.
+Lowe \etal \cite{Lowe2004} that proved a performance enhancement compared to a native matching strategy where only the nearest neighbour is considered.
+Once all matches for all queries are computed they are ranked and sorted according to the ${L_2}$ distance in one array.
+The correct matches are found by traversing the array of matches and count the number of matches that are spatial close, determined by a distance threshold.
+The PRC curves are presented in Section \ref{sec:evaluation} where precision refers to the number of correct matches compared to the total number of matches.
+Recall refers to the number of correct matches compared to the total amount of possible matches (i.e.
+feature seed points found in the target).
+In addition to PRC curves, we compute the area under the PRC curve (AUC) as a single quantitative measure of the overall accuracy.
+The AUC is computed as the numerical integration over all (P,R) per feature.
+%and the formula is presented in Equation \ref{eq::maxf1}.
+%Ratio of the nearest matching feature distance to that of the second nearest \cite{Buch2016}  
+%\begin{equation}\label{eq::maxf1}
+%max F_1 = {max}_{(P,R)} \left(2 \cdot \frac{P\cdot R}{P+R}\right)
+%\end{equation}
+\subsection{Pose estimation}
+In this section the experimental protocol for the pose estimation experiments is presented.
+The sampling and seed point selection are identical with the feature matching benchmark presented, except that we cannot use the ground truth pose for selecting target seed points.
+Instead, the target resolution is doubled, to quadruples the number of feature descriptors which increase the chance for describing the same feature.
+To increase the efficiency during matching we apply approximate nearest neighbour search to determine correspondences hypotheses instead of exact matching.
+Again, the ratio of the nearest and second nearest neighbours feature distances are used.
+A multiple randomized kd-trees with a bound of 512 checks and 4 trees are used as a good trade-off between accuracy and efficiency.
+Correspondences are ranked by the ${L_2}$ distance which inputs potential feature correspondences to a hypothesis and test RANSAC algorithm.
+During random sampling, three correspondences are sampled which is sufficient to generate a hypothesis pose.
+The hypothesis pose is tested by transforming the query points and counting the number of query points close to the target feature up to a tolerance given by the inlier threshold.
+The algorithm filters out false positives by setting a lower minimum of the number of inliers required to accept a pose hypothesis to 1\%.
+The pose with the highest number of inliers is returned as the object pose.
+Our RANSAC implementation deviates from classic RANSAC, which treats all data points uniformly.
+Instead we sample correspondences according to their quality score.
+The quality scores are given by the negative normalized ${L_2}$ distance ratio.
+The efficiency of the algorithm is further increased by only considering the top 10\% of the best correspondences with the highest quality score before running the RANSAC algorithm.
+Upon RANSAC completion the final pose is refined by 150 ICP iterations on the query/target seed points.
+We accept a pose estimate as valid by computing the euclidean and geodesic distances between the computed pose and the ground true pose from the annotation process.
+If the euclidean and geodesic distances are less than the threshold the object is correctly recognized.
+The euclidean and geodesic distance metrics are computed in accordance to Equation \ref{eq::rot} and \ref{eq::trans}.
+\begin{equation}\label{eq::rot}
+arccos \left(\frac{trace(\textbf{R}^{T}\hat{\textbf{R}})-1}{2}\right) \leq 7.5^\circ
+\end{equation}
+\begin{equation}\label{eq::trans}
+||\textbf{t} - \hat{\textbf{t}} || \leq 5mm
+\end{equation}
+The recognition rate is computed as the ratio of true positive poses compared to all detected poses as a quantitative measure of the overall recognition performance.
 %-------------------------------------------------------------------------
 \section{Evaluation}\label{sec:evaluation}
+In this section we present the results of our evaluation benchmark.
+All tests are based on the proposed dataset where 3204 scenes, 45 objects and 5675 ground truth poses are included.
+As a first evaluation we benchmark the matching accuracy of the seven feature descriptors with the parameters outlined in Section \ref{sec:benchmark_matching} and all 45 object models are included.
+The PRC curve of the overall matching accuracy is presented in Figure \ref{fig:all_L2_RATIO_zoom}.
+\begin{figure}[h]
+\includegraphics[clip, trim=0.7cm 6cm 0.7cm 6cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/all_L2_RATIO_zoom.pdf} 
+\caption{Overall PRC curve}\label{fig:all_L2_RATIO_zoom}
+\end{figure}
+As expected the total matching accuracy is much lower compared to previous studies e.g.
+Guo \etal \cite{Guo2015} and Buch \etal \cite{Buch2016}, which both are running a similar benchmark but on previous proposed datasets.
+The result indicate that our objective of the proposed dataset has been fulfilled.
+Moreover, the evaluation shows that the ECSAD feature has a best performance with a AUC = 0.046 followed by ROPS with AUC = 0.011.
+In order to investigate the performance further we run the matching benchmark for each quire and compute PRC curves for each of the 45 models.
+We have categorize the object into three different groups and present 3 PRC curves for each group in Figure \ref{fig:angel}-\ref{fig:noise} as a sample.
+The three groups are a) Geometric complex objects, b) Cylindrical objects and c) Flat or box shaped objects.
+The objects that corresponds to the PRC curves in Figure \ref{fig:angel}-\ref{fig:noise} are presented in Figure \ref{fig:selected_objects}.
+The geometric complex objects are the Angel, the Birds and the Rabbit in Figure \ref{fig:selected_objects}(a)-(c), the cylindrical objects are Neutral, Pringles and Hand soap in Figure \ref{fig:selected_objects}(d)-(f), and the flat or box shaped objects are the button, the brake disc and the Psu in Figure \ref{fig:selected_objects}(g)-(i).
+These PRC curves
 
+%As expected we see that all local shape feature in this benchmark have a hard time to establish correct matches 
+%Object recognition:
+%We first one run with a single query model.
+This is the hardest problem because we segment point belonging to a detected object away from the target.
+Thus, with more instances the individal matches are segmented first and therefor boost the probability for correct matches for the next object because objects beloning to the first object is remove from the target mesh.
+
+%"In general the matching accuracy of a descriptor is expected to increase with increasing support radius, except in cases where occlusion and clutter are present."
+
+\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
+\begin{table*}[hp]
+\centering
+\begin{tabular}{p{1.5cm} | P{1.1cm} | P{1.0cm} P{1.0cm} P{1.0cm} P{1.0cm} P{1.0cm} P{1.0cm} P{1.0cm} P{1.0cm} P{1.0cm} | P{1.0cm}}
+\hline
+\textbf{Feature} & \textbf{Overall} & \textbf{Angel} & \textbf{Birds} & \textbf{Rabbit} & \textbf{Neutral} & \textbf{Pringels} & \textbf{Hand soap} & \textbf{Button} & \textbf{Brake Disc} & \textbf{Psu}  & \textbf{\textit{Mean ($\lambda$)}} \\
+\hline
+\hline
+ \textbf{\textit{ECSAD}}  & 0.21  & \textbf{0.59} & \textbf{0.86} & \textbf{0.62} & 0.00 & 0.06 & 0.03 & 0.00 & 0.00 & 0.00 & 0.00\\
+ \textbf{\textit{FPFH}}   & 0.01  & 0.07 & 0.01 & 0.04 & 0.00 & 0.00 & 0.02 & 0.00 & 0.00 & 0.00 & 0.00\\
+ \textbf{\textit{NDHIST}} & 0.02  & 0.13 & 0.05 & 0.14 & \textbf{0.02} & \textbf{0.06} & 0.02 & 0.00 & 0.00 & 0.00 & 0.00\\
+ \textbf{\textit{ROPS}}   & 0.13  & 0.45 & 0.70 & 0.29 & 0.01 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
+ \textbf{\textit{SHOT}}   & 0.04  & 0.25 & 0.09 & 0.14 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
+ \textbf{\textit{SI}}     & 0.05  & 0.20 & 0.16 & 0.10 & 0.01 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
+ \textbf{\textit{USC}}    & 0.00  & 0.01 & 0.04 & 0.09 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
+%\textbf{\textit{PFH}}    & 0.00 \vline  & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
+%\textbf{\textit{3DSC}}   & 0.00 \vline  & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
+ \hline
+\end{tabular}
+\label{tab:recognition}
+\caption{Overall recognition rates.
+\textbf{Column 1:} Features descriptors.
+\textbf{Column 2:} Overall recognition rate.
+\textbf{Column 3-11:} Recognition rate for each sample object in Figure \ref{fig:selected_objects}.
+\textbf{Column 12:} Mean recognition rate for the 9 sample object per.
+feature.}
+\end{table*}
+
+\begin{figure*}[bp]
+	\centering
+	\begin{subfigure}[Ecsad]{%{0.18\textwidth}
+		\includegraphics[clip, trim=6.7cm 1cm 6.7cm 3.5cm,width=0.3\linewidth, height= 0.25\linewidth, keepaspectratio]{img/ecsad_1.png}
+		%\subcaption{Angel}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+	\begin{subfigure}[Ndhist]{%{.18\textwidth}	
+		\includegraphics[clip, trim=5cm 1cm 5cm 1cm,width=0.3\linewidth, height= 0.25\linewidth, keepaspectratio]{img/ndhist.png}
+		%\caption{Birds}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+	\begin{subfigure}[Rops]{%{.18\textwidth}
+		\includegraphics[clip, trim=4cm 1cm 7cm 1.7cm,width=0.3\linewidth, height= 0.25\linewidth, keepaspectratio]{img/rops.png}
+		%\subcaption{Rabbit}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+	\\
+	\begin{subfigure}[Shot]{%{.18\textwidth}	
+		\includegraphics[clip, trim=6cm 2cm 5cm 0.8cm,width=0.3\linewidth, height= 0.25\linewidth, keepaspectratio]{img/shot.png}
+		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+	\begin{subfigure}[Fpfh]{%{.18\textwidth}
+		\includegraphics[clip, trim=7.2cm 2cm 7.2cm 3.3cm,width=0.3\linewidth, height= 0.25\linewidth, keepaspectratio]{img/fpfh.png}
+		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+	\begin{subfigure}[Spin images]{%{.18\textwidth}
+		\includegraphics[clip, trim=4.2cm 2cm 6cm 0.2cm,width=0.3\linewidth, height= 0.25\linewidth, keepaspectratio]{img/si.png}
+		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+%	\begin{subfigure}[Usc]{%{.18\textwidth}
+%		\fbox{\includegraphics[clip, trim=6cm 1cm 5cm 1cm,width=0.2\linewidth, height= 0.25\linewidth, keepaspectratio]{img/ecsad_1.png}}
+%		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
+%		}
+%	\end{subfigure}
+	\captionsetup{justification=centering}
+\caption{Qualitative recognition results for scene 8}\label{fig:prc_curves}
+\end{figure*}
+%\section{Discussion}\label{sec:discussion}
+%-------------------------------------------------------------------------
+\section{Discussion \& Conclusion}\label{sec:conclusion}
+This paper has introduce a new large scale dataset for 3D object recognition and a evaluation benchmark to validate the dataset.
+Our benchmark results show as expected low matching scores for repetitive and symmetric objects.
+Further, objects with non-distinctive local geometric areas and thin edges results as expected in very low matching quality.
+From the evaluation we conclude that the dataset full-fill our requirement in terms of difficulty and that the objects ans scenes included represent the real world problems that a 3D object recognition system will face in the future.
+Our main goal of this work has been to span the real world 3D object recognition challenge that we face in especially in the flexible robotic automation industry.\\
+
+\clearpage
 \begin{figure*}[htp]
 	\centering
+	\begin{subfigure}[Angel]{%{0.18\textwidth}
+		\includegraphics[clip, trim=12cm 2cm 12cm 2cm,width=0.12\linewidth, height= 0.12\linewidth, keepaspectratio]{img/snapshot04.png}
+		%\subcaption{Angel}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+	\begin{subfigure}[Birds]{%{.18\textwidth}	
+		\includegraphics[clip, trim=12cm 2cm 12cm 2cm,width=0.12\linewidth, height= 0.12\linewidth, keepaspectratio]{img/snapshot05.png}
+		%\caption{Birds}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+	\begin{subfigure}[Rabbit]{%{.18\textwidth}
+		\includegraphics[clip, trim=12cm 2cm 12cm 2cm,width=0.12\linewidth, height= 0.12\linewidth, keepaspectratio]{img/snapshot07.png}
+		%\subcaption{Rabbit}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+	\begin{subfigure}[Neutral]{%{.18\textwidth}	
+		\includegraphics[clip, trim=12cm 2cm 12cm 2cm,width=0.12\linewidth, height= 0.12\linewidth, keepaspectratio]{img/snapshot08.png}
+		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+	\begin{subfigure}[Pringels]{%{.18\textwidth}
+		\includegraphics[clip, trim=12cm 2cm 12cm 2cm,width=0.12\linewidth, height= 0.12\linewidth, keepaspectratio]{img/snapshot14.png}
+		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+	\\
+	\begin{subfigure}[Hand soap]{%{.18\textwidth}
+		\includegraphics[clip, trim=12cm 2cm 12cm 2cm,width=0.12\linewidth, height= 0.12\linewidth, keepaspectratio]{img/snapshot17.png}
+		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+	\begin{subfigure}[Button]{%{.18\textwidth}
+		\includegraphics[clip, trim=12cm 2cm 12cm 2cm,width=0.12\linewidth, height= 0.12\linewidth, keepaspectratio]{img/snapshot22.png}
+		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+	\begin{subfigure}[Brake disc]{%{.18\textwidth}
+		\includegraphics[clip, trim=12cm 2cm 12cm 2cm,width=0.12\linewidth, height= 0.12\linewidth, keepaspectratio]{img/snapshot40.png}
+		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+	\begin{subfigure}[Psu]{%{.18\textwidth}
+		\includegraphics[clip, trim=12cm 2cm 12cm 2cm,width=0.12\linewidth, height= 0.12\linewidth, keepaspectratio]{img/snapshot24.png}
+		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
+		}
+	\end{subfigure}
+	\captionsetup{justification=centering}
+\caption{(a)-(c) Geometric complex objects used for dataset verification. (d)-(e) Cylinderical objects local. (f)-(h) Flat and box shaped objects}\label{fig:selected_objects}
+\end{figure*}
+
+\begin{figure*}[h]
 \begin{minipage}[b]{.3\textwidth}
-\includegraphics[width=1.0\linewidth, height= 0.7\linewidth, keepaspectratio]{img/PRC_1.pdf} 
-\caption{Noise level 1 for STL dataset}\label{fig:stl_n1}
+\includegraphics[clip, trim=0.7cm 6cm 0.7cm 6cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/5-Angel_L2_RATIO_zoom.pdf} 
+\caption{PRC curve: Angel }\label{fig:angel}
 \end{minipage}\qquad
 \begin{minipage}[b]{.3\textwidth}
-\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
-\caption{Noise level 2 for STL dataset}\label{fig:stl_n2}
+\includegraphics[clip, trim=0.7cm 6cm 0.7cm 6cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/6-Birds_L2_RATIO_zoom.pdf}
+\caption{PRC curve: Birds }\label{fig:birds}
 \end{minipage}
 \begin{minipage}[b]{.3\textwidth}
-\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
-\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
-\end{minipage}
-\begin{minipage}[b]{.3\textwidth}
-\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf} 
-\caption{Decimination level 1 for STL dataset}\label{fig:stl_d1}
-\end{minipage}\qquad
-\begin{minipage}[b]{.3\textwidth}
-\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
-\caption{Decimination level 2 for STL dataset}\label{fig:stl_d2}
-\end{minipage}
-\begin{minipage}[b]{.3\textwidth}
-\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
-\caption{Decimination level 3 for STL dataset}\label{fig:stl_d3}
+\includegraphics[clip, trim=0.7cm 6cm 0.7cm 6cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/8-Rabbit_L2_RATIO_zoom.pdf}
+\caption{PRC curve: Rabbit }\label{fig:rabbit}
 \end{minipage}
@@
 
-\begin{figure*}[htp]
-\centering
+\begin{figure*}[h]
 \begin{minipage}[b]{.3\textwidth}
-\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf} 
-\caption{Noise level 1 for Kinect dataset}\label{fig:kinect_n1}
+\includegraphics[clip, trim=0.7cm 6cm 0.7cm 6cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/9-Neutral_L2_RATIO_zoom.pdf} 
+\caption{PRC curve: Neutral }\label{fig:neutral}
 \end{minipage}\qquad
 \begin{minipage}[b]{.3\textwidth}
-\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
-\caption{Noise level 2 for Kinect dataset}\label{fig:kinect_n2}
+\includegraphics[clip, trim=0.7cm 6cm 0.7cm 6cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/15-Pringles_L2_RATIO_zoom.pdf}
+\caption{PRC curve: Pringles}\label{fig:pringles}
 \end{minipage}
 \begin{minipage}[b]{.3\textwidth}
-\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
-\caption{Noise level 3 for Kinect dataset}\label{fig:kinect_n3}
-\end{minipage}
-\begin{minipage}[b]{.3\textwidth}
-\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf} 
-\caption{Decimination level 1 for Kinect dataset}\label{fig:kinect_d1}
-\end{minipage}\qquad
-\begin{minipage}[b]{.3\textwidth}
-\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
-\caption{Decimination level 2 for Kinect dataset}\label{fig:kinect_d2}
-\end{minipage}
-\begin{minipage}[b]{.3\textwidth}
-\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/PRC_1.pdf}
-\caption{Decimination level 3 for Kinect dataset}\label{fig:kinect_d3}
+\includegraphics[clip, trim=0.7cm 6cm 0.7cm 6cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/18-Hand_wash_L2_RATIO_zoom.pdf}
+\caption{PRC curve: Hand soap}\label{fig:hand_soap}
 \end{minipage}
@@
 
-%-------------------------------------------------------------------------
-\section{Discussion \& Conclusion}\label{sec:conclusion}
+\begin{figure*}[h]
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[clip, trim=0.7cm 6cm 0.7cm 6cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/23-Emergency_button_L2_RATIO_zoom.pdf} 
+\caption{PRC curve: Button }\label{fig:button}
+\end{minipage}\qquad
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[clip, trim=0.7cm 6cm 0.7cm 6cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/41-Brake_disc_L2_RATIO_zoom.pdf}
+\caption{PRC curve: Brake disc}\label{fig:brake disc}
+\end{minipage}
+\begin{minipage}[b]{.3\textwidth}
+\includegraphics[clip, trim=0.7cm 6cm 0.7cm 6cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/25-Psu_L2_RATIO_zoom.pdf}
+\caption{PRC curve: Psu}\label{fig:noise}
+\end{minipage}
+\end{figure*}
+
+%\textbf{Gr. 1}  &\textbf{Gr. 2} &\textbf{Gr. 3} p{0.8cm} p{0.8cm} p{0.8cm}
 
 %-------------------------------------------------------------------------
-
+\clearpage
 {\small

### 2016-07-13 paper.tex
almost finish

@@
 \begin{abstract}
-This paper presents a new large scale dataset suited for evaluation of local shape descriptors and 3d object recognition algorithms.
-The dataset consists of 3200 scenes and 45 different 3D object models.
-The individual scenes contain 10 occluded objects where the objects belongs to different geometric groups; concave, convex, cylindrical and flat 3D object models.
+This paper presents a new large scale dataset targeting evaluation of local shape descriptors and 3d object recognition algorithms.
+The dataset consists of point clouds and triangulated meshes from 292 physical scenes take from 11 different views; a total of approximately 3200 views.
+Each of the physical scenes contain 10 occluded objects resulting in a dataset with around 32000 unique object poses and 45 different object models.
+The 45 object models are full 360 degree models which are scanned with a high precision structured light scanner and a turntable.
+All the included objects belongs to different geometric groups; concave, convex, cylindrical and flat 3D object models.
 The object models have varying amount of local geometric features to challenge existing local shape feature descriptors in terms of descriptiveness and robustness.
@@
 Object recognition in range images is a fundamental research area in computer vision with many different applications in different industries.
-With the continually introduction of new inexpensive 3D sensors for different applications, the ability to localize and recognize rigid and no rigid objects is an attractive and unavoidable technology in the future.
+With the continually introduction of new inexpensive 3D sensors for different applications, the ability to localize and recognize rigid and no rigid objects is an attractive and unavoidable technology.
 Applications areas such as robotic assembly, bin-picking, mobile robotic manipulation, biometric analysis, tracking and intelligent surveillance all benefits from 3D data for localizing objects.
@@
 Until now, 3D object recognition algorithms are evaluated with eight smaller datasets \cite{Guo2015}, including in the UWA \cite{Mian2006},\cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2007} and Bologna \cite{Salti2014},\cite{Tombari2010} datasets.
-Other, smaller dataset like the Vienna Kinect\cite{Aldoma2012}, TUM \cite{Rodola2013}, TUM-LineMod\cite{Hinterstoisser2012}, BigBird\cite{BigBIRD} and RGB-D dataset version 1 \& 2\cite{Lai2011}, \cite{Lai2014} are proposed.
+Other, smaller dataset like the Vienna Kinect\cite{Aldoma2012}, TUM \cite{Rodola2013}, TUM-LineMod\cite{Hinterstoisser2012}, BigBird\cite{BigBIRD} and RGB-D dataset version 1 \& 2 \cite{Lai2011},\cite{Lai2014} are proposed.
 Common for all datasets is that the amount of scenes and/or models are limited.\\
-
-In this paper we present a new large-scale dataset consisting of 45 objects and 3200 scenes.
+\indent In this paper we present a new large-scale dataset consisting of 45 objects and 3200 views.
 The new dataset is recorded systematically in an environment without ambient light and with controlled illumination.
@@
 With this setup we are able to scan objects with an average point resolution of 275 microns.
-We validate our dataset by evaluating state of the art local shape features in a 3D object recognition pipeline.\\ %In Table \ref{tab:datasets} a summery of the features of ours and state of the art dataset are presented.\\
-\textit{Why does the 3D Object recognition community need another dataset?} Previous proposed datasets are limited in the total number of objects, object per.
+We validate our dataset by evaluating state of the art local shape features in a 3D object recognition pipeline.\\
+\indent \textit{Why does the 3D Object recognition community need another dataset?} Previous proposed datasets are limited in the total number of objects, object per.
 scene and total number of scenes.
 Additional, the included objects in the different datasets are mostly geometrical ideal objects.
-With geometrical ideal objects we refers to objects with concave water tight and closed surfaces that are rich of natural local descriptive geometrical features, like the UWA-chef model \cite{Mian2006},\cite{Mian2010}, the bologna-Armadillo \cite{Salti2014},\cite{Tombari2010} and the Queens-BigBird \cite{Taati2007},\cite{Taati2007}.
+With geometrical ideal objects we refers to objects with concave water tight and closed surfaces that are rich of local descriptive geometrical features, like the UWA-chef model \cite{Mian2006},\cite{Mian2010}, the bologna-Armadillo \cite{Salti2014},\cite{Tombari2010} and the Queens-BigBird \cite{Taati2007},\cite{Taati2007}.
 In our dataset we include not only ideal concave objects, but flat, cylindrical, feature-rich, simple concave and convex objects.
 It is expected that some local shape features will have a poor performance on our dataset because the lack of local geometric features.
-However, our main goal for proposing this dataset is to strengthen the focus on the challenges in 3D object recognition research and future algorithm development.
+However, our main goal for proposing this dataset is to highlight the challenges in 3D object recognition research and strengthen the data foundation in future algorithm development.
 This work is initiated because of previous experiences on pose estimation of geometric simple objects in an industrial robotic context.
@@
 Point Pair Features \cite{BirdalIlic2015}, semi-global features and template matching.
-
-Our objects are a combination of lab-objects and industrial objects, selected from companies that want to pick these objects from boxes or bins with a robot.\\
-This paper is structured as follows: In Section \ref{sec:related_work} related datasets and local feature descriptors are presented.
+We have selected the different objects based on previous experience, as a combination of lab-objects and industrial objects.
+The industrial objects are provided by companies that wish to pick the objects from boxes or bins with a robot.
+Thus, the dataset is a mix of objects that we know is problematic and objects from our lab which are more suited for in a 3D object recognition pipeline with local shape features.\\
+\indent This paper is structured as follows: In Section \ref{sec:related_work} related datasets and local feature descriptors are presented.
 Section \ref{sec:exp_design} outlines our experimental design followed by Section \ref{sec:benchmark} which presents our benchmarking methodology.
@@
 \begin{table*}[ht]
-\label{tab:datasets}
 \centering % Center table
@@
 %        \captionof{table}{Existing datasets for 3D object recognition and pose estimation}% Add 'table' caption
-        \label{tab:dataset_overview}
-
 \caption{Comparison of existing datasets for 3D object recognition with the presented datasets.
@@
 }
+\label{tab:dataset_overview}
 \end{table*}
@@
 %We are not considering learning approaches
+We will now relate our work to state of the art. First, we review existing 3D object recognition datasets followed by a concise review of significant local feature descriptors.\\
+
 \noindent
@@
 These datasets are widely used in performance evaluations of  local feature descriptors \cite{Guo2015}, \cite{Buch2016}, keypoint detectors \cite{Salti2011} and surveys \cite{Guo2014}, \cite{FilipeAlexandre2014}.
-The main problems of all the datasets are; size, variety of objects and occlusion/clutter estimates.
-The recent comparison studies \cite{Buch2016},\cite{Guo2015} revival that the data for evaluation is not good enough to scientific distinguish results.
-The studies showed that the performance of one local feature descriptor is poor when evaluated on one dataset but fail in other datasets.
-These results reveal that a larger data foundation is required in the quest to find shape features which generalize over many object categories.\\
+The main problems of all the datasets are; size, variety of objects, few objects per.
+scene and missing occlusion/clutter estimates.
+For object recognition in 2.5D, where either a full object model or sampled templates are used for recognizing object in a color and depth image, is not considered in this work.
+However, some datasets exist for this problem e.g.
+the Line-Mod dataset \cite{Hinterstoisser2012}.\\
 
@@
 Designing descriptors which are distinctive and robust to occlusion and noise is still an ongoing research topic.
-Recent studies have shown that the proposed features are not generalizing well over many types of geometry classes, \cite{Guo2015},\cite{Buch2016}.
+
+\indent Local feature descriptors aim at computing a distinctive and robust N-dimensional feature vector around a point, by considering the points in an Euclidean neighbourhood.
+The support radius determining the size of the neighbourhood is often one of the critical parameters in the pipeline.
+Local feature descriptors are often split into two different categories, spatial and geometrical histograms \cite{Salti2014}.
+Recent studies have shown that the state of the art features are not generalizing well over many types of geometry classes, \cite{Guo2015},\cite{Buch2016}.
 The studies proved one of the main issues in 3D object recognition today, namely the fact that there exist no local shape feature that describes the geometry well over many different object classes, e.g.
@@
 What feature(s) to use are still dependent on the object geometry.
-These studies pose a relevant research question; are the local feature descriptors not descriptive enough to generalize over different object classes or are the data used for evaluation too limited?
+However, the experimental result in \cite{Buch2016} showed the advantage of fusing several local feature descriptors.
+The studies from \cite{Guo2015},\cite{Buch2016} leave a relevant research question to be answered; are the local feature descriptors not descriptive enough to generalize over different object classes or are the data used for evaluation too limited?
 The evaluation datasets used for the evaluation in general and in \cite{Guo2015},\cite{Buch2016} consist mainly of objects with many descriptive and distinctive geometrical features.\\
-Local feature descriptors aim at computing a distinctive and robust N-dimensional feature vector around a point, by considering the points in an Euclidean neighbourhood.
-The support radius determining the size of the neighbourhood is often one of the critical parameters in the pipeline.
-Local feature descriptors are often split into two different categories, spatial and geometrical histograms \cite{Salti2014}.
-%Global feature descriptors, typical computes a descriptors by considering the spatial and/or geometrical relations between two or more local feature descriptors on a 3D geometry.
-{\color{blue} TS I would remove the last sentence about global descriptors.}
-
-%and pose estimation \cite{Viksten09}, \cite{Hinterstoisser2012}, this kind of scientific validations of results still lacks in 3D object recognition. 
-%2D object recognition is well studied lacking with 3D. Keypoint comparison Aan{\ae}s et.al. \cite{Aanaes2011}
-
-%We study the performance of the top six local shape features and one global descriptor 
-%Limitations in current dataset and algorithms. Feature rich objects not flat or cylindrical objects
+%The recent comparison studies \cite{Buch2016},\cite{Guo2015} revival that the data for evaluation is not good enough to scientific distinguish results.
+The studies showed that the performance of one local feature descriptor is poor when evaluated on one dataset but fail in other datasets.
+These results reveal that a larger data foundation is required in the quest to find shape features which generalize over many object categories.\\
 %------------------------------------------------------------------------
@@
 %Describe the object scanning process
-\subsection{Object model scanning}
+We have constructed a dataset by achieving highly accurate 3D model of each of the 45 individual objects, as described in Section \ref{sec:object_scanning}.
+These are then used to compose 292 individual scenes where 10 objects are placed in different configurations.
+A robot moves our scanner to 11 fixed positions in order to create 11 independent view points of the same object configuration, as described in Section \ref{sec:scene_scanning}.
+Hence, we have 3200 individual observations of 10 objects included in the dataset.
+We argue that these observations are independent because of the large view point change at 36 degree horizontal and 45 degree vertical.
+Thus, the objects surface are very different in each view.
+We achieve very accurate ground truth poses by annotating the entire dataset with our high resolution object models in full resolution, as described in Section \ref{sec:gt_pose}.
+\subsection{Object model scanning}\label{sec:object_scanning}
 Our object models are scanned with a high precision structured light setup consisting of two industrial cameras (Point Grey Research GS3-U3-91S6C-C) and
@@
 Each of the 45 objects are incremental scanned with a rotation of 20 degrees.
+\begin{figure}[htp]
+\centering
+\includegraphics[clip, trim=1cm 1cm 1cm 1.3cm,width=0.9\linewidth, height= 0.4\linewidth, keepaspectratio]{img/objects/objects.pdf}
+\caption{A sample of the scanned object models}
+\label{fig:objects}
+\end{figure}
 All individual scan views are reconstructed by the Line shifting algorithm \cite{Guehring2000} which results in accurate and dense point cloud of the objects.
@@
 Note that the modelling setup is not radiometrical calibrated.
-\begin{figure}[ht]
-\centering
-\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/objects/objects.pdf}
-\caption{Four of the fifty scanned and triangulated object models}
-\label{fig:objects}
-\end{figure}
+
 %Describe setup for scene aqusition
-\subsection{Scene scanning} 
+\subsection{Scene scanning}\label{sec:scene_scanning}
 For the data collection we use a 6-axis ABB IRB 1600 industrial robot to provide a precise and highly repeatable camera pose.
-The robot is depicted in Figure \ref{fig:robot}.
 The robot is equipped with two PointGray Grasshopper3 GS3-U391S6C-C USB3 color cameras with resolution of 9.1 Mp and a Wintech Pro4500 projector with a resolution of 1140x912 pixels.
@@
 Second, Time-of-Flight sensors like the Kinect One sensor are popular sensors in many research areas such as robotic manipulation, 3D semantic mapping, people detection and consumer products thus we wanted to support the future development of 3D object recognition systems and algorithms by including the sensor in the dataset.
-\begin{figure}[ht]
-\centering
-\includegraphics[width=1.0\linewidth, height= 0.7\linewidth]{Robot.pdf}
-\caption{Scan of the full scene with view frames}
-\label{fig:robot}
-\end{figure}
+%\begin{figure}[ht]
+%\centering
+%\includegraphics[width=0.9\linewidth, height= 0.6\linewidth]{Robot.pdf}
+%\caption{Scan of the full scene with view frames}
+%\label{fig:robot}
+%\end{figure}
 The Robot setup is constructed as a radiometric "dead" which gives a scene representation with zero ambient light.
@@
 \centering
-\includegraphics[clip, trim=12cm 6cm 12cm 8cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/mesh_scene.png}
+\includegraphics[clip, trim=14cm 6cm 13cm 8cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/mesh_scene.png}
 \caption{Example on one of the 3200 triangulated scene}
@@
 %A Note on ground truth
-\subsection{Ground Truth 6D pose}
+\subsection{Ground Truth 6D pose}\label{sec:gt_pose}
 For each of the 3200 scenes the 6D ground truth pose, occlusion and clutter estimates for each object are provided.
@@
 %\end{equation}
-\subsection{Pose estimation}
+\subsection{Pose estimation}\label{sec:pose_estimation}
 In this section the experimental protocol for the pose estimation experiments is presented.
@@
 In this section we present the results of our evaluation benchmark.
-All tests are based on the proposed dataset where 3204 scenes, 45 objects and 5675 ground truth poses are included.
-As a first evaluation we benchmark the matching accuracy of the seven feature descriptors with the parameters outlined in Section \ref{sec:benchmark_matching} and all 45 object models are included.
+All experiments are based on the proposed dataset where 3204 scenes, 45 objects and 5675 ground truth poses are included.
+As a first evaluation we benchmark the matching accuracy of the seven feature descriptors with the parameters outlined in Section \ref{sec:benchmark_matching} and all 45 object models included.
 The PRC curve of the overall matching accuracy is presented in Figure \ref{fig:all_L2_RATIO_zoom}.
@@
 Moreover, the evaluation shows that the ECSAD feature has a best performance with a AUC = 0.046 followed by ROPS with AUC = 0.011.
-In order to investigate the performance further we run the matching benchmark for each quire and compute PRC curves for each of the 45 models.
+In order to investigate the performance further we run the matching benchmark for each object model and compute PRC curves for each of the 45 models.
 We have categorize the object into three different groups and present 3 PRC curves for each group in Figure \ref{fig:angel}-\ref{fig:noise} as a sample.
@@
 The geometric complex objects are the Angel, the Birds and the Rabbit in Figure \ref{fig:selected_objects}(a)-(c), the cylindrical objects are Neutral, Pringles and Hand soap in Figure \ref{fig:selected_objects}(d)-(f), and the flat or box shaped objects are the button, the brake disc and the Psu in Figure \ref{fig:selected_objects}(g)-(i).
-These PRC curves
-
-%As expected we see that all local shape feature in this benchmark have a hard time to establish correct matches 
-%Object recognition:
-%We first one run with a single query model.
-This is the hardest problem because we segment point belonging to a detected object away from the target.
-Thus, with more instances the individal matches are segmented first and therefor boost the probability for correct matches for the next object because objects beloning to the first object is remove from the target mesh.
-
-%"In general the matching accuracy of a descriptor is expected to increase with increasing support radius, except in cases where occlusion and clutter are present."
-
+The results show that a recent precision and recall are achieved with the Angel,Birds and Rabbit, but it is much lower than previous studies e.g.
+Buch \etal \cite{Buch2016} that obtain very matching accuracy for some datasets.
+These low numbers for our geometric ideal objects indicate that the proposed dataset have the desired level of complexity.
+Regarding, the cylindrical objects which features the Neutral, Pringles and Hand Soap objects, it is clear that current local shape descriptors is very little descriptive for these uniform shaped objects.
+Again, ECSAD performs in general best which might results from the fact that ECSAD describes edges in a good way.
+For the flat and boxed shaped models we can conclude that current state of the art feature descriptors is not suitable as the only detection method.\\
+\indent The result for the pose estimation experiments are presented in Table \ref{tab:recognition} and Figure \ref{fig:pose_est_results}.
+Our object recognition pipeline in these experiment is in accordance to the presented pipeline in Section \ref{sec:pose_estimation}.
 \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
-\begin{table*}[hp]
+\begin{table*}[t]
 \centering
-\begin{tabular}{p{1.5cm} | P{1.1cm} | P{1.0cm} P{1.0cm} P{1.0cm} P{1.0cm} P{1.0cm} P{1.0cm} P{1.0cm} P{1.0cm} P{1.0cm} | P{1.0cm}}
+\scalebox{0.8}{
+\begin{tabular}{p{1.25cm} | P{1.1cm} | P{1.4cm} P{1.4cm} P{1.4cm} P{1.4cm} P{1.4cm} P{1.7cm} P{1.4cm} P{1.65cm} P{1.4cm} | P{1.4cm}}
 \hline
@@
 \end{tabular}
-\label{tab:recognition}
+}
 \caption{Overall recognition rates.
@@
 feature.}
+\label{tab:recognition}
 \end{table*}
-
-\begin{figure*}[bp]
+\begin{figure*}[t]
 	\centering
 	\begin{subfigure}[Ecsad]{%{0.18\textwidth}
-		\includegraphics[clip, trim=6.7cm 1cm 6.7cm 3.5cm,width=0.3\linewidth, height= 0.25\linewidth, keepaspectratio]{img/ecsad_1.png}
+		\includegraphics[clip, trim=6.7cm 1cm 6.7cm 3.5cm,width=0.3\linewidth, height= 0.2\linewidth, keepaspectratio]{img/ecsad_1.png}
 		%\subcaption{Angel}\label{fig:stl_n3}
@@
 	\begin{subfigure}[Ndhist]{%{.18\textwidth}	
-		\includegraphics[clip, trim=5cm 1cm 5cm 1cm,width=0.3\linewidth, height= 0.25\linewidth, keepaspectratio]{img/ndhist.png}
+		\includegraphics[clip, trim=5cm 1cm 5cm 1cm,width=0.3\linewidth, height= 0.2\linewidth, keepaspectratio]{img/ndhist.png}
 		%\caption{Birds}\label{fig:stl_n3}
@@
 	\begin{subfigure}[Rops]{%{.18\textwidth}
-		\includegraphics[clip, trim=4cm 1cm 7cm 1.7cm,width=0.3\linewidth, height= 0.25\linewidth, keepaspectratio]{img/rops.png}
+		\includegraphics[clip, trim=4cm 1cm 7cm 1.7cm,width=0.3\linewidth, height= 0.2\linewidth, keepaspectratio]{img/rops.png}
 		%\subcaption{Rabbit}\label{fig:stl_n3}
@@
 	\begin{subfigure}[Shot]{%{.18\textwidth}	
-		\includegraphics[clip, trim=6cm 2cm 5cm 0.8cm,width=0.3\linewidth, height= 0.25\linewidth, keepaspectratio]{img/shot.png}
+		\includegraphics[clip, trim=6cm 2cm 5cm 0.8cm,width=0.3\linewidth, height= 0.2\linewidth, keepaspectratio]{img/shot.png}
 		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
@@
 	\begin{subfigure}[Fpfh]{%{.18\textwidth}
-		\includegraphics[clip, trim=7.2cm 2cm 7.2cm 3.3cm,width=0.3\linewidth, height= 0.25\linewidth, keepaspectratio]{img/fpfh.png}
+		\includegraphics[clip, trim=7.2cm 2cm 7.2cm 3.3cm,width=0.3\linewidth, height= 0.2\linewidth, keepaspectratio]{img/fpfh.png}
 		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
@@
 	\begin{subfigure}[Spin images]{%{.18\textwidth}
-		\includegraphics[clip, trim=4.2cm 2cm 6cm 0.2cm,width=0.3\linewidth, height= 0.25\linewidth, keepaspectratio]{img/si.png}
+		\includegraphics[clip, trim=4.2cm 2cm 6cm 0.2cm,width=0.3\linewidth, height= 0.2\linewidth, keepaspectratio]{img/si.png}
 		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
@@
 	\captionsetup{justification=centering}
-\caption{Qualitative recognition results for scene 8}\label{fig:prc_curves}
+\caption{Qualitative recognition results for scene 8}\label{fig:pose_est_results}
 \end{figure*}
-%\section{Discussion}\label{sec:discussion}
-%-------------------------------------------------------------------------
+In the first recognition experiment we run the pipeline with all 45 object model included and present the recognition rate in Table \ref{tab:recognition}, second column.
+In the second experiment we run the recognition benchmark for each individual object, which is a harder problem because we remove scene points upon each detected object.
+Hence, we reduce the number of scene point for each match even when the algorithm recognize false positives which results in removal of false point in the scene.
+Again, as expected Ecsad and Rops performs best on average.
+However, the recognition rate is lower than seen in other datasets which is expected since some views in our dataset is heavy occluded.
+In Figure \ref{fig:pose_est_results} qualitative results are presented for the recognition result in scene 8.
+Again, is is clear that Ecad and rops performing best with 4 and 2 correct recognize object, respectively.
+
 \section{Discussion \& Conclusion}\label{sec:conclusion}

### 2016-10-02 paper.tex
IJCV template

@@
 This paper presents a new large scale dataset targeting evaluation of local shape descriptors and 3d object recognition algorithms.
-The dataset consists of point clouds and triangulated meshes from 292 physical scenes take from 11 different views; a total of approximately 3200 views.
-Each of the physical scenes contain 10 occluded objects resulting in a dataset with around 32000 unique object poses and 45 different object models.
+The dataset consists of point clouds and triangulated meshes from 292 physical scenes taken from 11 different views; a total of approximately 3204 views.
+Each of the physical scenes contain 10 occluded objects resulting in a dataset with 32040 unique object poses and 45 different object models.
 The 45 object models are full 360 degree models which are scanned with a high precision structured light scanner and a turntable.
-All the included objects belongs to different geometric groups; concave, convex, cylindrical and flat 3D object models.
+All the included objects belong to different geometric groups; concave, convex, cylindrical and flat 3D object models.
 The object models have varying amount of local geometric features to challenge existing local shape feature descriptors in terms of descriptiveness and robustness.
@@
 It is our objective that this dataset contributes to the future development of next generation of 3D object recognition algorithms.
-The dataset will be made public available.
+The dataset will be made public available together with this paper.
 \end{abstract}
@@
 \section{Introduction} %Hvad, hvorfor, hvordan
-Object recognition in range images is a fundamental research area in computer vision with many different applications in different industries.
+Object recognition from range images is a fundamental research area in computer vision with many different applications in different industries.
 With the continually introduction of new inexpensive 3D sensors for different applications, the ability to localize and recognize rigid and no rigid objects is an attractive and unavoidable technology.
@@
 Common for all datasets is that the amount of scenes and/or models are limited.\\
-\indent In this paper we present a new large-scale dataset consisting of 45 objects and 3200 views.
+\indent In this paper we present a new large-scale dataset consisting of 45 objects and 3204 views.
 The new dataset is recorded systematically in an environment without ambient light and with controlled illumination.
 The system includes an industrial robot in a dark chamber, a high precision structured light scanner which records data of 292 different scenes from 11 different view points.
-Each scene consists of 10 occluded objects, automatic taken with the structured light sensor, which results in a dataset with around 32000 unique object poses.
+Each scene consists of 10 occluded objects, automatically taken with a structured light sensor, which results in a dataset with 32040 unique object poses.
 With 11 different views of the same scene our dataset is especially suited for studying the effect of view point changes in 3D object recognition.
-The objects are configured as a classic table-top scenario where different objects are depicted for the side.
+The objects are configured as a classic table-top scenario where different objects are depicted form the side.
 The dataset is not meant as an evaluation platform for bin-picking and top-view scenarios where many instances of the same object are present in the scene.
-The table-top scenario is selected because it encapsulate many of the problems and challenges in 3D object recognition in favour of a larger research community.
+The table-top scenario is selected because it encapsulates many of the problems and challenges in 3D object recognition in favour of a larger research community.
 Our 45 object models are scanned in a similar dark chamber with a high precision structured light scanner and a rotation table.
@@
 Additional, the included objects in the different datasets are mostly geometrical ideal objects.
-With geometrical ideal objects we refers to objects with concave water tight and closed surfaces that are rich of local descriptive geometrical features, like the UWA-chef model \cite{Mian2006},\cite{Mian2010}, the bologna-Armadillo \cite{Salti2014},\cite{Tombari2010} and the Queens-BigBird \cite{Taati2007},\cite{Taati2007}.
+With geometrical ideal objects we refer to objects with concave water tight and closed surfaces that are rich of local descriptive geometrical features, like the UWA-chef model \cite{Mian2006},\cite{Mian2010}, the bologna-Armadillo \cite{Salti2014},\cite{Tombari2010} and the Queens-BigBird \cite{Taati2007},\cite{Taati2007}.
 In our dataset we include not only ideal concave objects, but flat, cylindrical, feature-rich, simple concave and convex objects.
@@
 However, our main goal for proposing this dataset is to highlight the challenges in 3D object recognition research and strengthen the data foundation in future algorithm development.
-This work is initiated because of previous experiences on pose estimation of geometric simple objects in an industrial robotic context.
-We hope that new novel methods for 3D object recognition will emerge in the future as a side-effect of this dataset.
-Not only local shape descriptos but to a great extend features that uses point relations across the surface e.g.
+This work is initiated by our previous experiences on pose estimation of geometric simple objects in an industrial robotic context.
+We hope that new novel methods for 3D object recognition will emerge in the future, as a side-effect of this dataset.
+Not only local shape descriptors but to a great extend features that use point relations across the surface e.g.
 Point Pair Features \cite{BirdalIlic2015}, semi-global features and template matching.
 We have selected the different objects based on previous experience, as a combination of lab-objects and industrial objects.
-The industrial objects are provided by companies that wish to pick the objects from boxes or bins with a robot.
-Thus, the dataset is a mix of objects that we know is problematic and objects from our lab which are more suited for in a 3D object recognition pipeline with local shape features.\\
+The industrial objects are provided by companies that need to pick the objects from boxes or bins with a robot.
+Thus, the dataset is a mix of real industrial objects that we know from experience is difficult to detect and objects from our lab which are more suited for a 3D object recognition pipeline with local shape features.\\
 \indent This paper is structured as follows: In Section \ref{sec:related_work} related datasets and local feature descriptors are presented.
@@
              \hline
-             Queens Lidar  \cite{Taati2011}, \cite{Taati2007}  & 5 & 80 & LIDAR & (1-5)/(1-5) & \checkmark  & \checkmark & \%  & 0 & \checkmark & \% & \% & R\\
+             Queens Lidar  \cite{Taati2011}, \cite{Taati2007}  & 5 & 80 & LIDAR & (1-5)/(1-5) & \checkmark  & \checkmark & \%  & \checkmark & \checkmark & \% & \% & R\\
              \hline
-             Queens Stereo  \cite{Taati2011}, \cite{Taati2007}  & 5 & 100 & Stereo & (3)/(3)   & \checkmark & \checkmark & \%  & 0 & \checkmark & \% & \% & R\\
+             Queens Stereo  \cite{Taati2011}, \cite{Taati2007}  & 5 & 100 & Stereo & (3)/(3)   & \checkmark & \checkmark & \%  & \checkmark & \checkmark & \% & \% & R\\
              \hline
@@
              \hline
-             Vienna Kinect \cite{Aldoma2012} & 35 & 50 & Kinect V1 & 0 & \checkmark & \checkmark & \% & 0 & \checkmark & \% & \% & R\\
+             Vienna Kinect \cite{Aldoma2012} & 35 & 50 & Kinect V1 & (1-5)/(1-5) & \checkmark & \checkmark & \% & \% & \checkmark & \% & \% & R\\
              \hline
-             RGB-D Scenes V1 \cite{Lai2011}, \cite{Lai2012} & 5 & 8 videos & Kinect V1 & (0)/ & \% & \%  & \%  & \% & \% & \% & \% & R\\
+             RGB-D Scenes V1 \cite{Lai2011}, \cite{Lai2012} & 5 & 8 videos & Kinect V1 & (0)/(5) & \% & \%  & \%  & \% & \% & \% & \% & R\\
 			 \hline             
-             RGB-D Scenes V2 \cite{Lai2014} & 9 & 14 & Kinect V1 & (0)/ & \% & \% & \% & \% & \% & \% & \% & R\\
+             RGB-D Scenes V2 \cite{Lai2014} & 9 & 14 & Kinect V1 & (0)/(9) & \% & \% & \% & \% & \% & \% & \% & R\\
              \hline
@@
              \hline
-             Willow \cite{Willow} & 35 & 177 & Kinect V1 & 0 & \checkmark  & \checkmark  & \% & 0 & \% & \% & \% & R\\
+             Willow \cite{Willow} & 35 & 177 & Kinect V1 & * & \checkmark  & \checkmark  & \% & \% & \% & \% & \% & R\\
              \hline
@@
              \hline
-              Alicante \cite{Garcia-Garcia2016}  & 30 & 50 & Kinect V2 & (0)/(0) & \% & \checkmark  & \% & 0 & \checkmark & \% & \% & R\\
+              Alicante \cite{Garcia-Garcia2016}  & 28 & 9 & Kinect V2 & * & \% & \checkmark  & \% & 0 & \checkmark & \% & \% & R\\
              \hline
              \hline
-             \textbf{Our dataset}  & \textbf{45} & \textbf{3200} & SL & (10)/(10) & \checkmark  & \checkmark  & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark & R\\
+             \textbf{Our dataset}  & \textbf{45} & \textbf{3204} & SL & (10)/(10) & \checkmark  & \checkmark  & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark & R\\
           %   \hline
@@
 \caption{Comparison of existing datasets for 3D object recognition with the presented datasets.
-{$M_q$} is the amount of different models in the dataset and {$S_t$} is the amount of scenes.[R]/[S] indicates whether the dataset is synthetic or acquired in real world.
-}
+{$M_q$} is the amount of different models in the dataset and {$S_t$} is the amount of scenes.
+{$M_q$} in {$S_t$} shows how many models annotated in each scene and how many objects there are in each scene (No.
+annotated in scene/No.
+of object in scene).[R]/[S] indicates whether the dataset is synthetic or acquired in the real world.
+\textit{(* dataset unavailable online)}}
 \label{tab:dataset_overview}
@@
 Common for all existing dataset are the limited number of 3D object models and scenes.
-A comparison of the different datasets are presented in Table \ref{tab:dataset_overview}.
+A comparison of the different datasets are presented in Table \ref{tab:dataset_overview}, from which it is seen that our dataset is magnitudes larger.
 The most common used datasets are the UWA  \cite{Mian2006}, \cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2011} and the Bologna \cite{Salti2014}, \cite{Tombari2010}.
@@
 scene and missing occlusion/clutter estimates.
-For object recognition in 2.5D, where either a full object model or sampled templates are used for recognizing object in a color and depth image, is not considered in this work.
+In this work we are not considering 2.5D recognition methods where either a full object model or sampled templates is used for recognizing object in a RGB-D image.
 However, some datasets exist for this problem e.g.
-the Line-Mod dataset \cite{Hinterstoisser2012}.\\
+the Line-Mod dataset \cite{Hinterstoisser2012} or the recent published RGB-D dataset for warehouse pick-and-place tasks \cite{Rennie2015}.\\
 
@@
 The descriptors find usages in applications such as 3D object categorization, recognition, retrieval, analysis, registration and reconstruction among others.
-Designing descriptors which are distinctive and robust to occlusion and noise is still an ongoing research topic.
+Designing descriptors which are distinctive and robust toward occlusion and noise is still an ongoing research topic.
 
@@
 Recent studies have shown that the state of the art features are not generalizing well over many types of geometry classes, \cite{Guo2015},\cite{Buch2016}.
-The studies proved one of the main issues in 3D object recognition today, namely the fact that there exist no local shape feature that describes the geometry well over many different object classes, e.g.
+The studies proved one of the main issues in 3D object recognition today, that there exist no local shape feature which describes the geometry well over many different object classes, e.g.
 flat, rotational symmetrical and geometrically feature rich objects.
 What feature(s) to use are still dependent on the object geometry.
-However, the experimental result in \cite{Buch2016} showed the advantage of fusing several local feature descriptors.
-The studies from \cite{Guo2015},\cite{Buch2016} leave a relevant research question to be answered; are the local feature descriptors not descriptive enough to generalize over different object classes or are the data used for evaluation too limited?
+However, the experimental results in \cite{Buch2016} showed the advantage of fusing several local feature descriptors.
+The studies from \cite{Guo2015},\cite{Buch2016} leave a relevant research question to be answered; are the local feature descriptors not descriptive enough to generalize different object classes or are the data used for evaluation too limited?
 The evaluation datasets used for the evaluation in general and in \cite{Guo2015},\cite{Buch2016} consist mainly of objects with many descriptive and distinctive geometrical features.\\
@@
 A robot moves our scanner to 11 fixed positions in order to create 11 independent view points of the same object configuration, as described in Section \ref{sec:scene_scanning}.
-Hence, we have 3200 individual observations of 10 objects included in the dataset.
+Hence, we have 3204 individual observations of 10 objects included in the dataset.
 We argue that these observations are independent because of the large view point change at 36 degree horizontal and 45 degree vertical.
@@
 a high resolution DLP projector (LG PF80G) mounted on a rigid aluminium frame. 
-In addition, a high precision turntable (Newmark Systems RT-5) is used in order to provide automatic rotation of the object.
-Each of the 45 objects are incremental scanned with a rotation of 20 degrees.
 \begin{figure}[htp]
@@
 \end{figure}
-All individual scan views are reconstructed by the Line shifting algorithm \cite{Guehring2000} which results in accurate and dense point cloud of the objects.
+In addition, a high precision turntable (Newmark Systems RT-5) is used in order to provide automatic rotation of the object.
+Each of the 45 objects are incremental scanned with a rotation of 20 degrees.
+All individual scan views are reconstructed by the Line shifting algorithm \cite{Guehring2000}, which results in accurate and dense point clouds of the objects.
 Eleven temporal binary gray code patterns are projected followed by eight line shifting patterns.
@@
 \includegraphics[clip, trim=14cm 6cm 13cm 8cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/mesh_scene.png}
-\caption{Example on one of the 3200 triangulated scene}
+\caption{Example on one of the 3204 triangulated scene}
 \label{fig:mesh_scene}
@@
 \subsection{Ground Truth 6D pose}\label{sec:gt_pose}
-For each of the 3200 scenes the 6D ground truth pose, occlusion and clutter estimates for each object are provided.
+For each of the 3204 scenes the 6D ground truth pose, occlusion and clutter estimates for each object are provided.
 We estimate the occlusion from Equation \ref{eq:occlusion} and clutter from Equation \ref{eq:clutter} by counting the number of points at the object model in which the squared euclidean distance to a scene point is less than two times the scene resolution.
@@
 This full scene point cloud is applied in the annotation process, see Figure \ref{fig:scene}.
-The full scene point cloud covers the geometric structures of each model in the scene with more point compared to the individual views.
+The full scene point cloud covers the geometric structures of each model in the scene with more points compared to the individual views.
 Thus, it is possible to get a more accurate ICP registration of the object model in the scenes.
-All 290 combined scenes are manual annotated by selecting four identical points for each model and the scene, followed by an estimation of the rigid transform.
+All 290 combined scenes are manually annotated by selecting four identical points for each model and the scene, followed by an estimation of the rigid transform.
 An iterative ICP, which incremental decreases the allowed correspondence distance ensures a very accurate final ground truth pose of each object in the scene.
@@
 The individual ground truth poses in each sensor view $T_{sensor_{n}}$ is computed by transforming the ground truth poses from the world frame $T_{world}$ to each of the individual sensor frames $T_{sensor_{n}}$.
-Equation \ref{eq:transformation} show the final transformation.
+Equation \ref{eq:transformation} shows the final transformation.
 \begin{equation}
@@
 A feature descriptor for each seed point in the query and target mesh is computed.
-For fair comparison individually tuned support radii for each descriptors are used.
+For a fair comparison individually tuned support radii for each descriptors are used.
 We use the following feature resolution multiplier: SI($20$), 3DSC($22.5$), FPFH($17.5$), USC($25$), SHOT($17.5$), ROPS($20$), ECSAD($20$), NDHIST($31$).
@@
 The sampling and seed point selection are identical with the feature matching benchmark presented, except that we cannot use the ground truth pose for selecting target seed points.
-Instead, the target resolution is doubled, to quadruples the number of feature descriptors which increase the chance for describing the same feature.
+Instead, the target resolution is doubled, thus quadrupling the number of feature descriptors which increase the chance for describing the same feature.
 To increase the efficiency during matching we apply approximate nearest neighbour search to determine correspondences hypotheses instead of exact matching.
-Again, the ratio of the nearest and second nearest neighbours feature distances are used.
+Again, the ratio of the nearest and second nearest neighbour feature distances are used.
 A multiple randomized kd-trees with a bound of 512 checks and 4 trees are used as a good trade-off between accuracy and efficiency.
@@
 In this section we present the results of our evaluation benchmark.
-All experiments are based on the proposed dataset where 3204 scenes, 45 objects and 5675 ground truth poses are included.
+All experiments are based on the proposed dataset where 3204 views, 45 objects and 5675 ground truth poses are included.
 As a first evaluation we benchmark the matching accuracy of the seven feature descriptors with the parameters outlined in Section \ref{sec:benchmark_matching} and all 45 object models included.
@@
 As expected the total matching accuracy is much lower compared to previous studies e.g.
-Guo \etal \cite{Guo2015} and Buch \etal \cite{Buch2016}, which both are running a similar benchmark but on previous proposed datasets.
-The result indicate that our objective of the proposed dataset has been fulfilled.
+Guo \etal \cite{Guo2015} and Buch \etal \cite{Buch2016}, where both are running a similar benchmark but on previous proposed datasets.
+The result indicates that our objective of the proposed dataset has been fulfilled.
 Moreover, the evaluation shows that the ECSAD feature has a best performance with a AUC = 0.046 followed by ROPS with AUC = 0.011.
@@
 The geometric complex objects are the Angel, the Birds and the Rabbit in Figure \ref{fig:selected_objects}(a)-(c), the cylindrical objects are Neutral, Pringles and Hand soap in Figure \ref{fig:selected_objects}(d)-(f), and the flat or box shaped objects are the button, the brake disc and the Psu in Figure \ref{fig:selected_objects}(g)-(i).
-The results show that a recent precision and recall are achieved with the Angel,Birds and Rabbit, but it is much lower than previous studies e.g.
-Buch \etal \cite{Buch2016} that obtain very matching accuracy for some datasets.
-These low numbers for our geometric ideal objects indicate that the proposed dataset have the desired level of complexity.
-Regarding, the cylindrical objects which features the Neutral, Pringles and Hand Soap objects, it is clear that current local shape descriptors is very little descriptive for these uniform shaped objects.
-Again, ECSAD performs in general best which might results from the fact that ECSAD describes edges in a good way.
+The results show that a recent precision/recall is achieved with the Angel,Birds and Rabbit, but it is much lower than previous studies e.g.
+Buch \etal \cite{Buch2016} who obtain very matching accuracy for some datasets.
+These low numbers for our geometric ideal objects indicate that the our dataset has the desired level of complexity.
+Regarding, the cylindrical objects which features the Neutral, Pringles and Hand Soap objects, it is clear that current local shape descriptors are very little descriptive for these uniform shaped objects.
+Again, ECSAD performs in general best which might results from ECSAD' ability to capture edges.
 For the flat and boxed shaped models we can conclude that current state of the art feature descriptors is not suitable as the only detection method.\\
-\indent The result for the pose estimation experiments are presented in Table \ref{tab:recognition} and Figure \ref{fig:pose_est_results}.
+\indent The results for the pose estimation experiments are presented in Table \ref{tab:recognition} and Figure \ref{fig:pose_est_results}.
 Our object recognition pipeline in these experiment is in accordance to the presented pipeline in Section \ref{sec:pose_estimation}.
@@
 \centering
-\scalebox{0.8}{
-\begin{tabular}{p{1.25cm} | P{1.1cm} | P{1.4cm} P{1.4cm} P{1.4cm} P{1.4cm} P{1.4cm} P{1.7cm} P{1.4cm} P{1.65cm} P{1.4cm} | P{1.4cm}}
+\scalebox{0.78}{
+\begin{tabular}{p{1.25cm} | P{1.1cm} | P{1.4cm} P{1.4cm} P{1.4cm} | P{1.4cm} P{1.4cm} P{1.7cm} | P{1.4cm} P{1.65cm} P{1.4cm} | P{1.4cm}}
 \hline
@@
 \hline
- \textbf{\textit{ECSAD}}  & 0.21  & \textbf{0.59} & \textbf{0.86} & \textbf{0.62} & 0.00 & 0.06 & 0.03 & 0.00 & 0.00 & 0.00 & 0.00\\
- \textbf{\textit{FPFH}}   & 0.01  & 0.07 & 0.01 & 0.04 & 0.00 & 0.00 & 0.02 & 0.00 & 0.00 & 0.00 & 0.00\\
- \textbf{\textit{NDHIST}} & 0.02  & 0.13 & 0.05 & 0.14 & \textbf{0.02} & \textbf{0.06} & 0.02 & 0.00 & 0.00 & 0.00 & 0.00\\
- \textbf{\textit{ROPS}}   & 0.13  & 0.45 & 0.70 & 0.29 & 0.01 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
- \textbf{\textit{SHOT}}   & 0.04  & 0.25 & 0.09 & 0.14 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
- \textbf{\textit{SI}}     & 0.05  & 0.20 & 0.16 & 0.10 & 0.01 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
- \textbf{\textit{USC}}    & 0.00  & 0.01 & 0.04 & 0.09 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
+ \textbf{\textit{ECSAD}}  & 0.21  & \textbf{0.59} & \textbf{0.86} & \textbf{0.62} & 0.00 & 0.06 & \textbf{0.03} & 0.00 & 0.00 & 0.00 & \textbf{0.24}\\
+ \textbf{\textit{FPFH}}   & 0.01  & 0.07 & 0.01 & 0.04 & 0.00 & 0.00 & 0.02 & 0.00 & 0.00 & 0.00 & 0.02\\
+ \textbf{\textit{NDHIST}} & 0.02  & 0.13 & 0.05 & 0.14 & \textbf{0.02} & \textbf{0.06} & 0.02 & 0.00 & 0.00 & 0.00 & 0.05\\
+ \textbf{\textit{ROPS}}   & 0.13  & 0.45 & 0.70 & 0.29 & 0.01 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.16\\
+ \textbf{\textit{SHOT}}   & 0.04  & 0.25 & 0.09 & 0.14 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.05\\
+ \textbf{\textit{SI}}     & 0.05  & 0.20 & 0.16 & 0.10 & 0.01 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.05\\
+ \textbf{\textit{USC}}    & 0.00  & 0.01 & 0.04 & 0.09 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.02\\
 %\textbf{\textit{PFH}}    & 0.00 \vline  & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
@@
 	\captionsetup{justification=centering}
-\caption{Qualitative recognition results for scene 8}\label{fig:pose_est_results}
+\caption{Qualitative recognition results for view 94}\label{fig:pose_est_results}
 \end{figure*}
 In the first recognition experiment we run the pipeline with all 45 object model included and present the recognition rate in Table \ref{tab:recognition}, second column.
-In the second experiment we run the recognition benchmark for each individual object, which is a harder problem because we remove scene points upon each detected object.
-Hence, we reduce the number of scene point for each match even when the algorithm recognize false positives which results in removal of false point in the scene.
-Again, as expected Ecsad and Rops performs best on average.
-However, the recognition rate is lower than seen in other datasets which is expected since some views in our dataset is heavy occluded.
-In Figure \ref{fig:pose_est_results} qualitative results are presented for the recognition result in scene 8.
-Again, is is clear that Ecad and rops performing best with 4 and 2 correct recognize object, respectively.
+In the second experiment we run the recognition benchmark for each individual object, which is a more complex problem because we in the benchmark remove the scene points corresponding to each detected object.
+Hence, in case of more objects to recognize, the number of scene points are reduced each time the algorithm detect an object.
+Again, as expected ECSAD and ROPS perform best on average.
+However, the recognition rate is lower than seen in other datasets which is expected since some views in our dataset are heavy occluded.
+In Figure \ref{fig:pose_est_results} qualitative results are presented for the recognition result in view 94.
+Again, is is clear that ECSAD and ROPS perform best with 4 and 2 correct recognize objects, respectively.
 
-\section{Discussion \& Conclusion}\label{sec:conclusion}
+\section{Conclusion}\label{sec:conclusion}
 This paper has introduce a new large scale dataset for 3D object recognition and a evaluation benchmark to validate the dataset.
-Our benchmark results show as expected low matching scores for repetitive and symmetric objects.
-Further, objects with non-distinctive local geometric areas and thin edges results as expected in very low matching quality.
-From the evaluation we conclude that the dataset full-fill our requirement in terms of difficulty and that the objects ans scenes included represent the real world problems that a 3D object recognition system will face in the future.
-Our main goal of this work has been to span the real world 3D object recognition challenge that we face in especially in the flexible robotic automation industry.\\
+Our benchmark results show as expected a general low matching score due to the level of complexity of the dataset.
+Especially, repetitive, symmetric, flat and thin-edge objects without many local features demonstrate as expected a very low precision/recall.
+Our matching results shows that the ECSAD feature performs best followed by the ROPS feature.
+This result is in accordance to some of the experiment in a previous benchmark by Buch \etal \cite{Buch2016}.
+Our object recognition results reflected as expected the low matching accuracy from the matching experiments.
+From the evaluation we conclude that the dataset full-fill our requirement in terms of difficulty.
+Furthermore, the objects and scenes included in the dataset represents the real world problems, which 3D object recognition systems need to handle in the future.
+Our main goal of this work has been to challenge existing 3D object recognition algorithms and create a dataset which contains real world object from the robot and automation industry.\\
 
@@
 	\captionsetup{justification=centering}
-\caption{(a)-(c) Geometric complex objects used for dataset verification. (d)-(e) Cylinderical objects local. (f)-(h) Flat and box shaped objects}\label{fig:selected_objects}
+\caption{(a)-(c) Geometric complex objects used for dataset verification. (d)-(e) Cylinderical objects. (f)-(h) Flat and box shaped objects}\label{fig:selected_objects}
 \end{figure*}
@@
 \begin{minipage}[b]{.3\textwidth}
+\includegraphics[clip, trim=0.7cm 6cm 0.7cm 6cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/25-Psu_L2_RATIO_zoom.pdf}
+\caption{PRC curve: Psu}\label{fig:noise}
+\end{minipage}
+\begin{minipage}[b]{.3\textwidth}
 \includegraphics[clip, trim=0.7cm 6cm 0.7cm 6cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/41-Brake_disc_L2_RATIO_zoom.pdf}
 \caption{PRC curve: Brake disc}\label{fig:brake disc}
-\end{minipage}
-\begin{minipage}[b]{.3\textwidth}
-\includegraphics[clip, trim=0.7cm 6cm 0.7cm 6cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/25-Psu_L2_RATIO_zoom.pdf}
-\caption{PRC curve: Psu}\label{fig:noise}
 \end{minipage}
